### 2015-01-20 paper/main.tex
template added

% Template for ICIP-2015 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{Machine learning techiniques for image classification - A Survey  }
%
% Single address.
% ---------------
\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
This paper explores the existing learning methods  in the area of image classification.
\end{abstract}
%
\begin{keywords}
One, two, three, four, five
\end{keywords}
%
\section{Introduction}
\label{sec:intro}
Image classification is the process of assigning one or more category label to an image or an image region.
Learning methods will 
These guidelines include complete descriptions of the fonts, spacing, and
related information for producing your proceedings manuscripts. Please follow
them and if you have any questions, direct them 
\texttt{info@icip2015.org}.

\section{Formatting your paper}
\label{sec:format}

All printed material, including text, illustrations, and charts, must be kept
within a print area of 178 mm (7 in.) wide by 229 mm (9 in.) high. Do
not write or print anything outside the print area. The top margin must be 25 mm (1
in.), except for the title page, and the left margin must be 19 mm (0.75 in.).  All {\it text} must be in a two-column format. Columns are to be 86 mm (3.39
in.) wide, with a 6 mm (0.24 in.) space between them. Text must be
fully justified.

\section{PAGE TITLE SECTION}
\label{sec:pagestyle}

The paper title (on the first page) should begin 35 mm (1.38 in.) from the
top edge of the page, centered, completely capitalized, and in Times 12-point,
boldface type. The authors' name(s) and affiliation(s) appear below the title
in capital and lower case letters. Papers with multiple authors and
affiliations may require two or more lines for this information. Please note
that papers should not be submitted blind; include the authors' names on the
PDF.

\section{TYPE-STYLE AND FONTS}
\label{sec:typestyle}

To achieve the best rendering both in printed proceedings and electronic proceedings, we
strongly encourage you to use Times-Roman font. In addition, this will give
the proceedings a more uniform look. Use a font that is no smaller than nine
point type throughout the paper, including figure captions.

In nine point type font, capital letters are 2 mm high. {\bf If you use the
smallest point size, there should be no more than 3.2 lines/cm (8 lines/in.)
vertically.} This is a minimum spacing; 2.75 lines/cm (7 lines/in.) will make
the paper much more readable. Larger type sizes require correspondingly larger
vertical spacing. Please do not double-space your paper. TrueType or
Postscript Type 1 fonts are preferred.

The first paragraph in each section should not be indented, but all the
following paragraphs within the section should be indented as these paragraphs
demonstrate.

\section{MAJOR HEADINGS}
\label{sec:majhead}

Major headings, for example, ``1. Introduction'', should appear in all capital
letters, bold face if possible, centered in the column, with one blank line
before, and one blank line after. Use a period (``.'') after the heading number,
not a colon.

\subsection{Subheadings}
\label{ssec:subhead}

Subheadings should appear in lower case (initial word capitalized) in
boldface. They should start at the left margin on a separate line.

\subsubsection{Sub-subheadings}
\label{sssec:subsubhead}

Sub-subheadings, as in this paragraph, are discouraged. However, if you
must use them, they should appear in lower case (initial word
capitalized) and start at the left margin on a separate line, with paragraph
text beginning on the following line.  They should be in italics.

\section{PAPER FORMAT}
\label{sec:print}

Format you paper for US letter, $8.5 \times 11$-in. paper.
A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
empty at the BOTTOM of the page and follow the top and left margins as
specified. If the last page of your paper is only partially filled, arrange
the columns so that they are evenly balanced if possible, rather than having
one long column.

In LaTeX, to start a new column (but not a new page) and help balance the
last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
demonstrated on this page (see the LaTeX source below).

\section{PAGE NUMBERING}
\label{sec:page}

Please do {\bf not} paginate your paper. Page numbers, session numbers, and
conference identification will be inserted when the paper is included in the
proceedings.

\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
\label{sec:illust}

Illustrations must appear within the designated margins. They may span the two
columns. If possible, position illustrations at the top of columns, rather
than in the middle or at the bottom.  Caption and number every illustration.
All halftone illustrations must be clear black and white prints. Colors may be
used, but they should be selected so as to be readable when printed on a
black-only printer.

Since there are many ways, often incompatible, of including images (e.g., with
experimental results) in a LaTeX document, below is an example of how to do
this \cite{Lamp86}.

\section{FOOTNOTES}
\label{sec:foot}

Use footnotes sparingly (or not at all!) and place them at the bottom of the
column on the page on which they are referenced. Use Times 9-point type,
single-spaced. To help your readers, avoid using footnotes altogether and
include necessary peripheral observations in the text (within parentheses, if
you prefer, as in this sentence).

% Below is an example of how to insert images. Delete the ``\vspace'' line,
% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
% with a suitable PostScript file name.
% -------------------------------------------------------------------------
\begin{figure}[t]

\begin{minipage}[b]{1.0\linewidth}
  \centering
  \centerline{\includegraphics[width=8.5cm]{Figures/image1}}
%  \vspace{2.0cm}
  \centerline{(a) Result 1}\medskip
\end{minipage}
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/image3}}
%  \vspace{1.5cm}
  \centerline{(b) Results 3}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/image4}}
%  \vspace{1.5cm}
  \centerline{(c) Result 4}\medskip
\end{minipage}
%
\caption{Example of placing a figure with experimental results.}
\label{fig:res}
%
\end{figure}

% To start a new column (but not a new page) and help balance the last-page
% column length use \vfill\pagebreak.
% -------------------------------------------------------------------------
%\vfill
%\pagebreak

\section{COPYRIGHT FORMS}
\label{sec:copyright}

You must include your fully completed, signed IEEE copyright release form when
form when you submit your paper. We {\bf must} have this form before your paper
can be published in the proceedings.

\section{REFERENCES}
\label{sec:ref}

List and number all bibliographical references at the end of the
paper. The references can be numbered in alphabetic order or in
order of appearance in the document. When referring to them in
the text, type the corresponding reference number in square
brackets as shown at the end of this sentence \cite{C2}. An
additional final page (the fifth page, in most cases) is
allowed, but must contain only references to the prior
literature.

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: refs). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}

### 2015-01-22 paper/survey.tex
completed 2nd paper

\documentclass{article}
\usepackage{amsmath,graphicx}

\begin{document}
\begin{section}{Deep Image: Scaling up Image Recognition}
The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al.\cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image. It uses a highly optimized parallel algorithm  to implement large deep neural network with augmented input data. The network is trained using stochastic gradient decent algorithms (SGD)[ref] on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs . System  uses an InfiniBand  network for interconnections. Parallelism strategies used in their network are model-data parallelism and data parallelism.  This methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.\cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems. But it is not easy extend the same strategies to multiple GPU cluster because of the communication overhead. So the  Baidu Team focused on minimizing network data transfers and overlapping the computation. They uses butterfly synchronization and lazy update strategies to achieve data parallelism in gradient computation. Their results shows model-data parallelism is better when number of GPUs is less than 16. Implementation of Data parallelism in large number  of GPU  cluster is better because of the constant communication requirements.
\par
The authors have explored different data augmentation techniques to increase the number of labeled images in the training set. This includes color casting, Vignetting , Lens distortion , Rotation , Flipping and  Cropping. Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging softmax class posteriors.
Data set used in this experiment was subset of ImageNet data set , used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{Berg2010}. This data set includes 1.2 million images which contains 1,000 categories.
\par
 Major contribution of this work is the demonstration of tremendous computational power to achieve high accuracy in image classification.
It also shows , augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification . 
 \end{section}
\section{VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION}
Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters. Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 x 2$ pixel window with stride 2. Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}. On the hardware side , it uses a multi-GPU system with NVIDIA Titan Black GPUs. Netwok is trained using multinomial logistic regression  based on back-propagation with momentum of 0.9 and  batch size  256.
\par
 In this work authors formed a conclusion that greater depth with small convolution filters and  preinitialization of certain layers will cause the learning process to converge in less number  of epochs. This model of convolution network does not differ from the classical architecture proposed by  LeCun et al.\cite{LeCun1998}. But the authors reported a significant improvement in the performance using an increased depth.  This implementation results in an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.

\section{Going deeper with convolutions Christian}

\section{REFERENCES}
\label{sec:survey}
\bibliographystyle{IEEEbib}
\bibliography{survey}

\end{document}

### 2015-01-23 paper/survey.tex
added a rank file
added two more paper from 2014

@@
 \begin{document}
+\section{notes}
+SPP is trying to avoid data augmentation . But the latest one introducing it model more sophisticated system.
+
+\section{Spatial pyramid pooling in Deep Convolutional Networks}
+Instead of using fixed input size in CNNs, Kaiming He et al.\cite{} suggested  a method to add  another spooling strategy called  spatial pyramid pooling(SPP) to avoid cropping or warping of  images .
+It introduced an new layer on top of convolution layer and perform aggregation  based on Bag-of-Words (BoW) model \cite{bow}.
+But the classical back propagation training methods expect layers to have fixed   size.
+To overcome this problem authors implemented two fixed size networks with shared parameters and switch the network on alternate epochs.
+This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
+\par 
+This implementation improves the performance of baseline architectures including ZF-5\cite{zf5} , Convnet \cite{Krizhevsky} and Overfeat-5/7 \cite{of}.
+Their study shows , accuracy of CNNs will improve on multi-size training, multi-level pooling and full-image representations.
+%
+
+\section{Going deeper with convolutions }
+Christian Szegedy and et al.\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244*244$ with number of layers around 100.
+Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs
+.
+Learning procedure took advantage of  model and data-parallelism in a CPU based cluster environment.
+This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set.
+Their result shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
+
+\section{VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION}
+Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
+Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 x 2$ pixel window with stride 2.
+Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}.
+On the hardware side , it uses a multi-GPU system with NVIDIA Titan Black GPUs.
+Netwok is trained using multinomial logistic regression  based on back-propagation with momentum of 0.9 and  batch size  256.
+\par
+ In this work authors formed a conclusion that greater depth with small convolution filters and  preinitialization of certain layers will cause the learning process to converge in less number  of epochs.
+This model of convolution network does not differ from the classical architecture proposed by  LeCun et al.\cite{LeCun1998}.
+But the authors reported a significant improvement in the performance using an increased depth.
+This implementation results in a significant improvement with  an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.
+
 \begin{section}{Deep Image: Scaling up Image Recognition}
@@
  \end{section}
-\section{VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION}
-Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
-Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 x 2$ pixel window with stride 2.
-Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}.
-On the hardware side , it uses a multi-GPU system with NVIDIA Titan Black GPUs.
-Netwok is trained using multinomial logistic regression  based on back-propagation with momentum of 0.9 and  batch size  256.
-\par
- In this work authors formed a conclusion that greater depth with small convolution filters and  preinitialization of certain layers will cause the learning process to converge in less number  of epochs.
-This model of convolution network does not differ from the classical architecture proposed by  LeCun et al.\cite{LeCun1998}.
-But the authors reported a significant improvement in the performance using an increased depth.
-This implementation results in an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.
-
-\section{Going deeper with convolutions Christian}
 

### 2015-01-23 paper/survey.tex
edited grammer

--- 2015-01-22 paper/survey.tex
@@
 \begin{document}
+\section{notes}
+SPP is trying to avoid data augmentation . But the latest one introducing it model more sophisticated system.
+
+\section{Spatial pyramid pooling in Deep Convolutional Networks}
+Instead of using fixed input size in CNNs, Kaiming He et al.\cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images.
+It introduced a new layer on top of the convolution layer and perform aggregation  based on Bag-of-Words (BoW) model \cite{Sivic2003}.
+But the classical back propagation training methods expect layers to have a fixed   size.
+To overcome this problem author implemented two fixed size networks with shared parameters and switch the network on alternate epochs.
+This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
+\par 
+This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}.
+Their study shows, accuracy of CNNs will improve on multi-size training, multi-level pooling, and full-image representations.
+%
+
+\section{Going deeper with convolutions }
+Christian Szegedy and et al.\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244*244$ with the number of layers around 100.
+Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs
+.
+Learning procedure took advantage of  model and data-parallelism in a CPU-based cluster environment.
+This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set.
+Their result shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
+
+\section{VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION}
+Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
+Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 x 2$ pixel window with stride 2.
+Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}.
+On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs.
+Network is trained using multinomial logistic regression  based on backpropagation with momentum of 0.9 and  batch size  256.
+\par
+ In this work authors formed a conclusion that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number  of epochs.
+This model of the convolution network does not differ from the classical architecture proposed by  LeCun et al.\cite{LeCun1998}.
+But the authors reported a significant improvement in the performance using an increased depth.
+This implementation results in a significant improvement in accuracy with  an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.
+
 \begin{section}{Deep Image: Scaling up Image Recognition}
@@
 Parallelism strategies used in their network are model-data parallelism and data parallelism.
-This methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.\cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems.
-But it is not easy extend the same strategies to multiple GPU cluster because of the communication overhead.
+These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.\cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems.
+But it is not easy extend the same strategies to multiple GPU clusters because of the communication overhead.
 So the  Baidu Team focused on minimizing network data transfers and overlapping the computation.
-They uses butterfly synchronization and lazy update strategies to achieve data parallelism in gradient computation.
-Their results shows model-data parallelism is better when number of GPUs is less than 16.
-Implementation of Data parallelism in large number  of GPU  cluster is better because of the constant communication requirements.
+They use butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation.
+Their results show model-data parallelism is better when number of GPUs is less than 16.
+Implementation of Data parallelism in a large number  of GPU  cluster is better because of the constant communication requirements.
 \par
 The authors have explored different data augmentation techniques to increase the number of labeled images in the training set.
-This includes color casting, Vignetting , Lens distortion , Rotation , Flipping and  Cropping.
-Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging softmax class posteriors.
-Data set used in this experiment was subset of ImageNet data set , used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{Berg2010}.
-This data set includes 1.2 million images which contains 1,000 categories.
+This includes color casting, Vignetting, Lens distortion, Rotation, Flipping, and  Cropping.
+Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft max class posteriors.
+Data set used in this experiment was subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{Berg2010}.
+This data set includes 1.2 million images which contain 1,000 categories.
 \par
  Major contribution of this work is the demonstration of tremendous computational power to achieve high accuracy in image classification.
-It also shows , augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification . 
+It also shows augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
  \end{section}
-\section{VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION}
-Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
-Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 x 2$ pixel window with stride 2.
-Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}.
-On the hardware side , it uses a multi-GPU system with NVIDIA Titan Black GPUs.
-Netwok is trained using multinomial logistic regression  based on back-propagation with momentum of 0.9 and  batch size  256.
-\par
- In this work authors formed a conclusion that greater depth with small convolution filters and  preinitialization of certain layers will cause the learning process to converge in less number  of epochs.
-This model of convolution network does not differ from the classical architecture proposed by  LeCun et al.\cite{LeCun1998}.
-But the authors reported a significant improvement in the performance using an increased depth.
-This implementation results in an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.
-
-\section{Going deeper with convolutions Christian}
 

### 2015-01-24 paper/survey.tex
started with 2013

@@
 SPP is trying to avoid data augmentation . But the latest one introducing it model more sophisticated system.
+Terms:dropout,maxout network
+Reducing filter size help to improve system.Increasing depth will help.
+
+\section{Network In Network }
+Inspired by the work of Ian J.
+Goodfellow et al.\cite{Goodfellow2013} on maxout networks,  Min Lin et al.\cite{{Lin2013} introduced a micro network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.
+
+\section{Visualizing and Understanding Convolutional Networks}
+
+Matthew D.
+Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of CNNs and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.\cite{Krizhevsky2012a}.
+This method helped  them  to understand  activation in the feature maps with respect to the input patterns.
+It shows Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
+Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%
 
@@
 \section{Going deeper with convolutions }
-Christian Szegedy and et al.\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244*244$ with the number of layers around 100.
+Christian Szegedy and et al.\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100.
 Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs
@@
 Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
-Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 x 2$ pixel window with stride 2.
+Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 \times 2$ pixel window with stride 2.
 Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}.

### 2015-01-24 paper/main.tex
added two more paper from 2014
started with intro

@@
 % ------
-\title{Machine learning techiniques for image classification - A Survey  }
+\title { Deep convolution networks for large scale image classification - A Survey  }
 %
@@
 fully justified.
+
+\section{Network In Network }
+Inspired by the work of Ian J.
+Goodfellow et al.\cite{Goodfellow2013} on maxout networks,  Min Lin et al.\cite{Lin2013} introduced a micro network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.
+
+Matthew D.
+Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of CNNs and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.\cite{Krizhevsky2012a}.
+This method helped  them  to understand  activation in the feature maps with respect to the input patterns.
+It shows Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
+Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%
+
+Instead of using fixed input size in CNNs, Kaiming He et al.\cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images.
+It introduced a new layer on top of the convolution layer and perform aggregation  based on Bag-of-Words (BoW) model \cite{Sivic2003}.
+But the classical back propagation training methods expect layers to have a fixed   size.
+To overcome this problem author implemented two fixed size networks with shared parameters and switch the network on alternate epochs.
+This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
+\par 
+This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}.
+Their study shows, accuracy of CNNs will improve on multi-size training, multi-level pooling, and full-image representations.
+%
+
+Christian Szegedy and et al.\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100.
+Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs
+.
+Learning procedure took advantage of  model and data-parallelism in a CPU-based cluster environment.
+This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set.
+Their result shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
+
+Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
+Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 \times 2$ pixel window with stride 2.
+Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}.
+On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs.
+Network is trained using multinomial logistic regression  based on backpropagation with momentum of 0.9 and  batch size  256.
+\par
+ In this work authors formed a conclusion that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number  of epochs.
+This model of the convolution network does not differ from the classical architecture proposed by  LeCun et al.\cite{LeCun1998}.
+But the authors reported a significant improvement in the performance using an increased depth.
+This implementation results in a significant improvement in accuracy with  an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.
+
+The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al.\cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image.
+It uses a highly optimized parallel algorithm  to implement large deep neural network with augmented input data.
+The network is trained using stochastic gradient decent algorithms (SGD)[ref] on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs .
+System  uses an InfiniBand  network for interconnections.
+Parallelism strategies used in their network are model-data parallelism and data parallelism.
+These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.\cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems.
+But it is not easy extend the same strategies to multiple GPU clusters because of the communication overhead.
+So the  Baidu Team focused on minimizing network data transfers and overlapping the computation.
+They use butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation.
+Their results show model-data parallelism is better when number of GPUs is less than 16.
+Implementation of Data parallelism in a large number  of GPU  cluster is better because of the constant communication requirements.
+\par
+The authors have explored different data augmentation techniques to increase the number of labeled images in the training set.
+This includes color casting, Vignetting, Lens distortion, Rotation, Flipping, and  Cropping.
+Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft max class posteriors.
+Data set used in this experiment was subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{Berg2010}.
+This data set includes 1.2 million images which contain 1,000 categories.
+\par
+ Major contribution of this work is the demonstration of tremendous computational power to achieve high accuracy in image classification.
+It also shows augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification.
 

### 2015-01-25 paper/survey.tex
started with CONVs

@@
 Reducing filter size help to improve system.Increasing depth will help. 
+\section{Multi-stage Hubel-Wiesel architecture}
+In 1962, Hubel DH and Wiesel TN\cite{Hubel1962},\cite{Hubel1965a} was studied visual cortex of anaesthetized cats  with   spots of white light of various shapes.
+They classified the  cells in the visual system in to  simple,complex and hypercomplex .
+Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field and  position of stimulus is important .
+This cells receives input from cells of the lateral geniculate nucleus(LGN), which is connected to retina.
+But the complex cells will responds to  a properly  oriented stimulus regardless of the cell position in the receptive field.
+Complex cells are activated by edge,dark bar,slit and mixed stimuli .
+Hypercomplex cells are activated by edge,single-stopped(corner),double-stopped (tongue),slit(double-stopped)and dark bar(double-stopped).
+
+\par Hubel DH and Wiesel TN \cite{Hubel1965a} presented a functional hierarchical structure of the visual cortex .
+According to their model, visual perception cells are in the  order , $simple\Longrightarrow complex\Longrightarrow lower \ order  \ hypercomplex  \Longrightarrow higher \ order \ hypercomplex$.
+Activation of  lower stage is  influenced by  the position of the input patterns and  higher stages are  position-invariant.
+There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
+\par Inspired by this work  , Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
+In neocognitron , cells are arranged in  a number of  cascded structure.
+Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$.
+This network is not affected by change in position or small distortion in the shape of patterns.
+It is also capable to do self organization based on an unsupervised competitive learning algorithm\cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
+\begin{figure}[ht]
+ \includegraphics[]{Figures/neocognitron.eps}
+\caption{Neocognitron\cite{Stark1980}}
+\label{neo}
+\end{figure}
+\par This design was improved by  Yann LeCun \cite{lecun-86},\cite{lecun-89d}, \cite{lecun-89e},\cite{lecun-90c}, \cite{lecun-90e} using backpropagation algorithm\cite{BRYSON1963} to train the entire system.
+
+%2012
+
+%2013
 
@@
 Inspired by the work of Ian J.
-Goodfellow et al.\cite{Goodfellow2013} on maxout networks,  Min Lin et al.\cite{{Lin2013} introduced a micro network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.
+Goodfellow et al.\cite{Goodfellow2013} on maxout networks,  Min Lin et al.\cite{Lin2013} introduced a micro network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the newtork.
 
@@
 Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%
+
+%2014
 

### 2015-01-25 paper/survey.tex
started intro

--- 2015-01-24 paper/survey.tex
@@
 Reducing filter size help to improve system.Increasing depth will help.
+\section{Introduction}
+
+\section{Multi-stage Hubel-Wiesel architecture}
+In 1962, Hubel DH and Wiesel TN\cite{Hubel1962},\cite{Hubel1965a} was studied visual cortex of anesthetized cats  with   spots of white light of various shapes.
+They classified the  cells in the visual system into  simple, complex and hypercomplex.
+Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field, and  position of the stimulus is important.
+This cell receives input from cells of the lateral geniculate nucleus(LGN), which is connected to the retina.
+However, the complex cells will responds to  a properly  oriented stimulus regardless of the cell position in the receptive field.
+Complex cells are activated by edge, dark bar, slit and mixed stimuli.
+Hypercomplex cells are activated by edge,single-stopped(corner),double-stopped (tongue),slit(double-stopped)and dark bar(double-stopped).
+
+\par Hubel DH and Wiesel TN \cite{Hubel1965a} presented a functional hierarchical structure of the visual cortex.
+According to their model, visual perception cells are in the  order, $simple\Longrightarrow complex\Longrightarrow lower \ order  \ hypercomplex  \Longrightarrow higher \ order \ hypercomplex$.
+Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant.
+There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
+\par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
+In neocognitron , cells are arranged in  a number of  cascaded structure.
+Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$.
+This network is not affected by change in position or small distortion in the shape of patterns.
+It is also capable of doing self-organization based on an unsupervised competitive learning algorithm\cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
+\begin{figure}[ht]
+ \includegraphics[]{Figures/neocognitron.eps}
+\caption{Neocognitron\cite{Stark1980}}
+\label{neo}
+\end{figure}
+\section{Convolutional Networks}
+\par Neocognitron was improved by  Yann LeCun \cite{lecun-86},\cite{lecun-89d}, \cite{lecun-89e},\cite{lecun-90c}, \cite{lecun-90e} using backpropagation algorithm\cite{BRYSON1963} to train the entire system.
+It uses  local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance.
+A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al..\cite{LeCun1998}  for document recognition.
+Using local receptive fields network can extract elementary visual features such as edges, end point, and corners.
+This features will combine to obtain high order features in the following layers.
+Elementary feature detectors with identical weights can be useful in different parts of the image.
+So the units with  the same set of weights are arranged in plane and output from  the units of a plane is called  a feature map.
+Units in  a feature map perform the same operation on different parts of the same image.
+A convolution layer is composed of the set of feature maps with differently weighed units.
+In the implementation, a unit in the feature map scans the image and store the states in the feature map.
+This operation is equivalent to convolution with a kernel composed of a  set of weights and image.
+
+\par
+A typical convolutional  network composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
+\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between a input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
+. ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$. Where $b_j$ is a trainable bias , $i$ and $j$ are  array indices.\\
+\emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output.
+But to reduce training time with gradient decent, new implementations uses the function $max(0,x)$.
+Units with this non-linearity is called Rectified Linear Units (ReLUs)\cite{Nair2010}.\\
+\emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
+
+\section {Deep convolutional networks}
+In last few years convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST\cite{Ciresan:2012g},CIFAR-10,CIFAR-100,SVHN\cite{lee2014deeply},STL-10 \cite{deepfwd}.
+One of the state-of-the-art error rate is from Krizhevsky, et al.\cite{Krizhevsky2012a}.Their network has 60 million parameters and 650,000 neurons, consists of five convolutional layers followed by max-pooling layers, and three fully-connected layers.
+
+%2012
+
+%2013
 
@@
 Inspired by the work of Ian J.
-Goodfellow et al.\cite{Goodfellow2013} on maxout networks,  Min Lin et al.\cite{{Lin2013} introduced a micro network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.
+Goodfellow et al..\cite{Goodfellow2013} on max out networks,  Min Lin et al.
+\cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network.
 
@@
 Matthew D.
-Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of CNNs and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.\cite{Krizhevsky2012a}.
-This method helped  them  to understand  activation in the feature maps with respect to the input patterns.
-It shows Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
+Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of CNNs and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.
+\cite{Krizhevsky2012a}.
+This method helped  them  to understand  the activation in the feature maps with respect to the input patterns.
+It shows Krizhevsky et al..'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
 Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%
 
+%2014
+
 \section{Spatial pyramid pooling in Deep Convolutional Networks}
-Instead of using fixed input size in CNNs, Kaiming He et al.\cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images.
+Instead of using fixed input size in CNNs, Kaiming He et al.
+\cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images.
 It introduced a new layer on top of the convolution layer and perform aggregation  based on Bag-of-Words (BoW) model \cite{Sivic2003}.
-But the classical back propagation training methods expect layers to have a fixed   size.
-To overcome this problem author implemented two fixed size networks with shared parameters and switch the network on alternate epochs.
+However, the classical backpropagation training methods expect layers to have a fixed   size.
+To overcome this problem author implemented two fixed size networks with shared parameters and switched the network on alternate epochs.
 This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
@@
 This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}.
-Their study shows, accuracy of CNNs will improve on multi-size training, multi-level pooling, and full-image representations.
+Their study shows; accuracy of CNNs will improve on multi-size training, multi-level pooling, and full-image representations.
 %
@@
 \section{Going deeper with convolutions }
-Christian Szegedy and et al.\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100.
+Christian Szegedy and et al.
+\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100.
 Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs
@@
  In this work authors formed a conclusion that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number  of epochs.
-This model of the convolution network does not differ from the classical architecture proposed by  LeCun et al.\cite{LeCun1998}.
+This model of the convolution network does not differ from the classical architecture proposed by  LeCun et  al.
+\cite{LeCun1998}.
 But the authors reported a significant improvement in the performance using an increased depth.
@@
 \begin{section}{Deep Image: Scaling up Image Recognition}
-The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al.\cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image.
+The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al.
+\cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image.
 It uses a highly optimized parallel algorithm  to implement large deep neural network with augmented input data.
@@
 Parallelism strategies used in their network are model-data parallelism and data parallelism.
-These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.\cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems.
-But it is not easy extend the same strategies to multiple GPU clusters because of the communication overhead.
+These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.
+\cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems.
+However, it is not easy extend the same strategies to multiple GPU clusters because of the communication overhead.
 So the  Baidu Team focused on minimizing network data transfers and overlapping the computation.
@@
 This includes color casting, Vignetting, Lens distortion, Rotation, Flipping, and  Cropping.
-Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft max class posteriors.
+Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft-max class posteriors.
 Data set used in this experiment was subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{Berg2010}.
-This data set includes 1.2 million images which contain 1,000 categories.
+This data set includes 1.2 million images that contain 1,000 categories.
 \par

### 2015-01-25 paper/main.tex
finished intro

@@
 \label{sec:intro}
-Image classification is the process of assigning one or more category label to an image or an image region.
-Learning methods will 
-These guidelines include complete descriptions of the fonts, spacing, and
-related information for producing your proceedings manuscripts. Please follow
-them and if you have any questions, direct them 
-\texttt{info@icip2015.org}.
+The performance of an  image  classification system mainly depends on the  extraction and  representation of features.
+Feature representation methods like Haralick texture features \cite{Haralick1973} got attention from the research community from the earlier days of  image classification.
+However, to develop features that are invariant to position, rotation, sailing, distortion and  illumination changes motivated researchers to  explore the visual perception of primates.
+This research  leads to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}.
+As a result, many successful image classification systems are  implemented with better accuracy \cite{lecun-89e}.
 
-\section{Formatting your paper}
-\label{sec:format}
+Early in that stage, method like the convolution network is limited by the  availability of labeled  data and computing infrastructure.
+However, in the recent years, the development of  High performance computing architecture such as general purpose graphical processing units (GPGPU )  accelerated the research in this field.
+Large scale image  dataset such as ImageNet\cite{imagenet}  with  millions of labeled samples is also accessible to the research community.
+This changes in data and computing, put back the convolution network with million of parameters in track.
 
-All printed material, including text, illustrations, and charts, must be kept
-within a print area of 178 mm (7 in.) wide by 229 mm (9 in.) high. Do
-not write or print anything outside the print area. The top margin must be 25 mm (1
-in.), except for the title page, and the left margin must be 19 mm (0.75 in.).  All {\it text} must be in a two-column format. Columns are to be 86 mm (3.39
-in.) wide, with a 6 mm (0.24 in.) space between them. Text must be
-fully justified.
+\section{Multi-stage Hubel-Wiesel architecture}
+In 1962, Hubel DH and Wiesel TN\cite{Hubel1962},\cite{Hubel1965a} was studied visual cortex of anesthetized cats  with   spots of white light of various shapes.
+They classified the  cells in the visual system into  simple, complex and hypercomplex.
+Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field, and  position of the stimulus is important.
+This cell receives input from cells of the lateral geniculate nucleus(LGN), which is connected to the retina.
+However, the complex cells will responds to  a properly  oriented stimulus regardless of the cell position in the receptive field.
+Complex cells are activated by edge, dark bar, slit and mixed stimuli.
+Hypercomplex cells are activated by edge,single-stopped(corner),double-stopped (tongue),slit(double-stopped)and dark bar(double-stopped).
+
+\par Hubel DH and Wiesel TN \cite{Hubel1965a} presented a functional hierarchical structure of the visual cortex.
+According to their model, visual perception cells are in the  order, simple$\Longrightarrow$ complex$\Longrightarrow$ lower order hypercomplex $\Longrightarrow$ higher  order hypercomplex.
+Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant.
+There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
+\par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
+In neocognitron , cells are arranged in  a number of  cascaded structure.
+Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$.
+This network is not affected by change in position or small distortion in the shape of patterns.
+It is also capable of doing self-organization based on an unsupervised competitive learning algorithm\cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
+\begin{figure}[ht]
+ \includegraphics[]{Figures/neocognitron.eps}
+\caption{Neocognitron\cite{Stark1980}}
+\label{neo}
+\end{figure}
+\section{Convolutional Networks}
+\par Neocognitron was improved by  Yann LeCun \cite{lecun-86},\cite{lecun-89d}, \cite{lecun-89e},\cite{lecun-90c}, \cite{lecun-90e} using backpropagation algorithm\cite{BRYSON1963} to train the entire system.
+It uses  local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance.
+A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al..\cite{LeCun1998}  for document recognition.
+Using local receptive fields network can extract elementary visual features such as edges, end point, and corners.
+This features will combine to obtain high order features in the following layers.
+Elementary feature detectors with identical weights can be useful in different parts of the image.
+So the units with  the same set of weights are arranged in plane and output from  the units of a plane is called  a feature map.
+Units in  a feature map perform the same operation on different parts of the same image.
+A convolution layer is composed of the set of feature maps with differently weighed units.
+In the implementation, a unit in the feature map scans the image and store the states in the feature map.
+This operation is equivalent to convolution with a kernel composed of a  set of weights and image.
+
+\par
+A typical convolutional  network composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
+\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between a input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
+. ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$. Where $b_j$ is a trainable bias , $i$ and $j$ are  array indices.\\
+\emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output.
+But to reduce training time with gradient decent, new implementations uses the function $max(0,x)$.
+Units with this non-linearity is called Rectified Linear Units (ReLUs)\cite{Nair2010}.\\
+\emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
+
+\section {Deep convolutional networks}
+In last few years convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST\cite{Ciresan:2012g},CIFAR-10,CIFAR-100,SVHN\cite{lee2014deeply},STL-10 \cite{deepfwd}.
+One of the state-of-the-art error rate is from Krizhevsky, et al.\cite{Krizhevsky2012a}.
+Their network has 60 million parameters and 650,000 neurons, consists of five convolutional layers followed by max-pooling layers, and three fully-connected layers.
+Data set used in this experiment was subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{imagenet}.
+This data set includes 1.2 million images that contain 1,000 categories.
+
+%2012
+
+%2013
 
@@
 Inspired by the work of Ian J.
-Goodfellow et al.\cite{Goodfellow2013} on maxout networks,  Min Lin et al.\cite{Lin2013} introduced a micro network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.
+Goodfellow et al..\cite{Goodfellow2013} on max out networks,  Min Lin et al.
+\cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network.
+
+\section{Visualizing and Understanding Convolutional Networks}
 
 Matthew D.
-Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of CNNs and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.\cite{Krizhevsky2012a}.
-This method helped  them  to understand  activation in the feature maps with respect to the input patterns.
-It shows Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
+Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of CNNs and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.
+\cite{Krizhevsky2012a}.
+This method helped  them  to understand  the activation in the feature maps with respect to the input patterns.
+It shows Krizhevsky et al..'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
 Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%
 
-Instead of using fixed input size in CNNs, Kaiming He et al.\cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images.
+%2014
+
+\section{Spatial pyramid pooling in Deep Convolutional Networks}
+Instead of using fixed input size in CNNs, Kaiming He et al.
+\cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images.
 It introduced a new layer on top of the convolution layer and perform aggregation  based on Bag-of-Words (BoW) model \cite{Sivic2003}.
-But the classical back propagation training methods expect layers to have a fixed   size.
-To overcome this problem author implemented two fixed size networks with shared parameters and switch the network on alternate epochs.
+However, the classical backpropagation training methods expect layers to have a fixed   size.
+To overcome this problem author implemented two fixed size networks with shared parameters and switched the network on alternate epochs.
 This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
@@
 This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}.
-Their study shows, accuracy of CNNs will improve on multi-size training, multi-level pooling, and full-image representations.
+Their study shows; accuracy of CNNs will improve on multi-size training, multi-level pooling, and full-image representations.
 %
 
-Christian Szegedy and et al.\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100.
+\section{Going deeper with convolutions }
+Christian Szegedy and et al.
+\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100.
 Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs
@@
 
+\section{VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION}
 Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
@@
 
-The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al.\cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image.
+\begin{section}{Deep Image: Scaling up Image Recognition}
+The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al.
+\cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image.
 It uses a highly optimized parallel algorithm  to implement large deep neural network with augmented input data.
@@
 This includes color casting, Vignetting, Lens distortion, Rotation, Flipping, and  Cropping.
-Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft max class posteriors.
-Data set used in this experiment was subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{Berg2010}.
-This data set includes 1.2 million images which contain 1,000 categories.
+Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft-max class posteriors.
+
 \par
@@
 It also shows augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
+ \end{section}
 
-\section{PAGE TITLE SECTION}
-\label{sec:pagestyle}
-
-The paper title (on the first page) should begin 35 mm (1.38 in.) from the
-top edge of the page, centered, completely capitalized, and in Times 12-point,
-boldface type. The authors' name(s) and affiliation(s) appear below the title
-in capital and lower case letters. Papers with multiple authors and
-affiliations may require two or more lines for this information. Please note
-that papers should not be submitted blind; include the authors' names on the
-PDF.
-
-\section{TYPE-STYLE AND FONTS}
-\label{sec:typestyle}
-
-To achieve the best rendering both in printed proceedings and electronic proceedings, we
-strongly encourage you to use Times-Roman font. In addition, this will give
-the proceedings a more uniform look. Use a font that is no smaller than nine
-point type throughout the paper, including figure captions.
-
-In nine point type font, capital letters are 2 mm high. {\bf If you use the
-smallest point size, there should be no more than 3.2 lines/cm (8 lines/in.)
-vertically.} This is a minimum spacing; 2.75 lines/cm (7 lines/in.) will make
-the paper much more readable. Larger type sizes require correspondingly larger
-vertical spacing. Please do not double-space your paper. TrueType or
-Postscript Type 1 fonts are preferred.
-
-The first paragraph in each section should not be indented, but all the
-following paragraphs within the section should be indented as these paragraphs
-demonstrate.
-
-\section{MAJOR HEADINGS}
-\label{sec:majhead}
-
-Major headings, for example, ``1. Introduction'', should appear in all capital
-letters, bold face if possible, centered in the column, with one blank line
-before, and one blank line after. Use a period (``.'') after the heading number,
-not a colon.
-
-\subsection{Subheadings}
-\label{ssec:subhead}
-
-Subheadings should appear in lower case (initial word capitalized) in
-boldface. They should start at the left margin on a separate line.
-
-\subsubsection{Sub-subheadings}
-\label{sssec:subsubhead}
-
-Sub-subheadings, as in this paragraph, are discouraged. However, if you
-must use them, they should appear in lower case (initial word
-capitalized) and start at the left margin on a separate line, with paragraph
-text beginning on the following line.  They should be in italics.
-
-\section{PAPER FORMAT}
-\label{sec:print}
-
-Format you paper for US letter, $8.5 \times 11$-in. paper.
-A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
-empty at the BOTTOM of the page and follow the top and left margins as
-specified. If the last page of your paper is only partially filled, arrange
-the columns so that they are evenly balanced if possible, rather than having
-one long column.
-
-In LaTeX, to start a new column (but not a new page) and help balance the
-last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
-demonstrated on this page (see the LaTeX source below).
-
-\section{PAGE NUMBERING}
-\label{sec:page}
-
-Please do {\bf not} paginate your paper. Page numbers, session numbers, and
-conference identification will be inserted when the paper is included in the
-proceedings.
-
-\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
-\label{sec:illust}
-
-Illustrations must appear within the designated margins. They may span the two
-columns. If possible, position illustrations at the top of columns, rather
-than in the middle or at the bottom.  Caption and number every illustration.
-All halftone illustrations must be clear black and white prints. Colors may be
-used, but they should be selected so as to be readable when printed on a
-black-only printer.
-
-Since there are many ways, often incompatible, of including images (e.g., with
-experimental results) in a LaTeX document, below is an example of how to do
-this \cite{Lamp86}.
-
-\section{FOOTNOTES}
-\label{sec:foot}
-
-Use footnotes sparingly (or not at all!) and place them at the bottom of the
-column on the page on which they are referenced. Use Times 9-point type,
-single-spaced. To help your readers, avoid using footnotes altogether and
-include necessary peripheral observations in the text (within parentheses, if
-you prefer, as in this sentence).
-
-% Below is an example of how to insert images. Delete the ``\vspace'' line,
-% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
-% with a suitable PostScript file name.
-% -------------------------------------------------------------------------
-\begin{figure}[t]
-
-\begin{minipage}[b]{1.0\linewidth}
-  \centering
-  \centerline{\includegraphics[width=8.5cm]{Figures/image1}}
-%  \vspace{2.0cm}
-  \centerline{(a) Result 1}\medskip
-\end{minipage}
-%
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{Figures/image3}}
-%  \vspace{1.5cm}
-  \centerline{(b) Results 3}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{Figures/image4}}
-%  \vspace{1.5cm}
-  \centerline{(c) Result 4}\medskip
-\end{minipage}
-%
-\caption{Example of placing a figure with experimental results.}
-\label{fig:res}
-%
-\end{figure}
-
-% To start a new column (but not a new page) and help balance the last-page
-% column length use \vfill\pagebreak.
-% -------------------------------------------------------------------------
-%\vfill
-%\pagebreak
-
-\section{COPYRIGHT FORMS}
-\label{sec:copyright}
-
-You must include your fully completed, signed IEEE copyright release form when
-form when you submit your paper. We {\bf must} have this form before your paper
-can be published in the proceedings.
-
-\section{REFERENCES}
-\label{sec:ref}
-
-List and number all bibliographical references at the end of the
-paper. The references can be numbered in alphabetic order or in
-order of appearance in the document. When referring to them in
-the text, type the corresponding reference number in square
-brackets as shown at the end of this sentence \cite{C2}. An
-additional final page (the fifth page, in most cases) is
-allowed, but must contain only references to the prior
-literature.
-
-% References should be produced using the bibtex program from suitable
-% BiBTeX files (here: refs). The IEEEbib.bst bibliography
-% style file from IEEE produces unsorted bibliography list.
-% -------------------------------------------------------------------------
 \bibliographystyle{IEEEbib}
-\bibliography{refs}
+\bibliography{survey}
 

### 2015-01-25 paper/main.tex
finished draft1

@@
 % ------
-\title { Deep convolution networks for large scale image classification - A Survey  }
+\title { Deep Convolutional networks for large scale image classification - A Survey  }
 %
@@
 % ---------------
-\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
+\name{Author(s) Name(s)}
 \address{Author Affiliation(s)}
@@
 \begin{abstract}
-This paper explores the existing learning methods  in the area of image classification.
+Image classification is an essential to the field of computer vision  based systems and recent research in this area explores better feature extraction, feature coding, and classification.
+The purpose of this paper is to review the application of supervised  deep convolution networks in this field.
+Numerous techniques have been reported to improve the performance of the convolution networks.
+It has been shown that with a large amount of labeled data, convolution networks can learn very complex functions such as image classification and speech recognition.
+
 \end{abstract}
@@
 \begin{keywords}
-One, two, three, four, five
+convolution networks, deep learning , neural networks.
 \end{keywords}
@@
 Feature representation methods like Haralick texture features \cite{Haralick1973} got attention from the research community from the earlier days of  image classification.
-However, to develop features that are invariant to position, rotation, sailing, distortion and  illumination changes motivated researchers to  explore the visual perception of primates.
+However, to develop features that are invariant to position, rotation, sailing, and distortion, researchers had  to  explore the visual perception of primates.
 This research  leads to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}.
@@
 
-Early in that stage, method like the convolution network is limited by the  availability of labeled  data and computing infrastructure.
+Early in that stage, method like the convolutional network is limited by the  availability of labeled  data and computing infrastructure.
 However, in the recent years, the development of  High performance computing architecture such as general purpose graphical processing units (GPGPU )  accelerated the research in this field.
@@
 \begin{figure}[ht]
- \includegraphics[]{Figures/neocognitron.eps}
+ \centering
+ \includegraphics[width=9cm]{Figures/neocognitron.eps}
 \caption{Neocognitron\cite{Stark1980}}
@@
 A typical convolutional  network composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
+\begin{figure}[ht]
+ \includegraphics[width=9.5cm]{Figures/convent.eps}
+\caption{A typical ConvNet architecture \cite{lecun2010convolutional}}
+\label{net}
+\end{figure}
 \emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between a input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
@@
 \emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8cm]{Figures/conv.eps}
+\caption{Output of  a randomly initialized   convolution filter. Input image courtesy:dcsku.org}
+\label{conv}
+\end{figure}
+
+%2012
 
@@
 Their network has 60 million parameters and 650,000 neurons, consists of five convolutional layers followed by max-pooling layers, and three fully-connected layers.
-Data set used in this experiment was subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{imagenet}.
+Data set used in this experiment was a subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{imagenet} and reported an error rate of 15.3\%.
 This data set includes 1.2 million images that contain 1,000 categories.
-
-%2012
 
@@
 
-\section{Network In Network }
+\subsection{Network In Network }
 Inspired by the work of Ian J.
@@
 
-\section{Visualizing and Understanding Convolutional Networks}
+\subsection{Visualizing Convolutional Networks}
 
 Matthew D.
-Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of CNNs and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.
+Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of convolutional networks and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.
 \cite{Krizhevsky2012a}.
@@
 It shows Krizhevsky et al..'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
-Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%
+Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.
 
@@
 
-\section{Spatial pyramid pooling in Deep Convolutional Networks}
-Instead of using fixed input size in CNNs, Kaiming He et al.
+\subsection{Spatial pyramid pooling in Deep Convolutional Networks}
+Instead of using fixed input size in convolutional networks, Kaiming He et al.
 \cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images.
@@
 This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}.
-Their study shows; accuracy of CNNs will improve on multi-size training, multi-level pooling, and full-image representations.
+Their study shows; accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations.
 %
 
-\section{Going deeper with convolutions }
+\subsection{Going deeper with convolutions }
 Christian Szegedy and et al.
@@
 
-\section{VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION}
+\section{VERY DEEP CONVOLUTIONAL NETWORKS }
 Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
@@
 
-\begin{section}{Deep Image: Scaling up Image Recognition}
+\begin{subsection}{Scaling up Image Classification}
 The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al.
@@
 It uses a highly optimized parallel algorithm  to implement large deep neural network with augmented input data.
-The network is trained using stochastic gradient decent algorithms (SGD)[ref] on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs .
+The network is trained using stochastic gradient decent algorithms (SGD on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs .
 System  uses an InfiniBand  network for interconnections.
@@
 It also shows augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
- \end{section}
+ \end{subsection}
+ \section {Summary}
+ \begin{enumerate}
+
+ \item Wisely chosen data  augmentation techniques can increase the performance of the network.
+ \item Data parallelism and model parallelism can increase the speed of the training process.
+ \item Greater depth with small convolution filters will improve the accuracy.
+ \item Network will get benefited from   image  in different scale .
+ \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural  level may reduce the error rate. 
+ \item  Rectified Linear Units can increase the speed of SGD.
+
+ \end{enumerate}
+
+ \begin{table}[h]
+ \begin{tabular}{ | p{5cm} | l | l |}
+    \hline
+Team	&Year	&Top 5 error\\
+    \hline
+        \hline
+Ren Wu et al.\cite{Wu2015}	&2015	&5.98\%\\
+    \hline
+Karen Simonyan and Andrew Zisserman.\cite{Arge2015}	&2014	&6.80\%\\
+    \hline
+Christian Szegedy and et al.\cite{Szegedy}	&2014	&6.67\%\\
+    \hline
+Kaiming He et al.\cite{He2014}	&2014	&8.06\%\\
+    \hline
+Matthew D. Zeiler and Rob Fergus \cite{Zeiler2013}	&2013	&11.74\%\\
+    \hline
+Min Lin et al.\cite{Lin2013}	&2013	&12.95\%\\
+    \hline
+Krizhevsky, et al.\cite{Krizhevsky2012a}	&2012	&15.30\%\\
+    \hline
+
+\end{tabular}
+\caption[]{ Top 5 error rate in ILSVRC}
+\end{table}
+
+\section{conclusion}
+This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance.
+Majority of the reviewed  works are reported from ImageNet Largqe-Scale Visual Recognition Challenge.
+There is no work exist to our knowledge, that explain all underpinning mathematics  of  deep convolutional  networks.
+This networks can only be trained using very expensive computing resources such as multiGPU cluster  to achieve more accuracy on large data sets.
+So  this research heavily depends on other research domains such as parallel algorithms, computer networks and multicore architecture.
+Because of the heavy computational requirements, it is not easy to apply this method directly  to the small level computing platforms such as embedded systems and application level  processors.
+On the other side, this methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.
 

### 2015-01-27 paper/main.tex
draft v2

@@
 Early in that stage, method like the convolutional network is limited by the  availability of labeled  data and computing infrastructure.
+Researchers are trying to overcome  this problem by many other non-parametric models such as SVM and KNN.
+But this methods couldn't give a high accuracy result  on any of  large-scale classification problem  and limited by the preprocessing technique.
 However, in the recent years, the development of  High performance computing architecture such as general purpose graphical processing units (GPGPU )  accelerated the research in this field.
@@
 In 1962, Hubel DH and Wiesel TN\cite{Hubel1962},\cite{Hubel1965a} was studied visual cortex of anesthetized cats  with   spots of white light of various shapes.
-They classified the  cells in the visual system into  simple, complex and hypercomplex.
+Cells in the visual system are classified    into  simple, complex and hypercomplex.
 Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field, and  position of the stimulus is important.
 This cell receives input from cells of the lateral geniculate nucleus(LGN), which is connected to the retina.
-However, the complex cells will responds to  a properly  oriented stimulus regardless of the cell position in the receptive field.
+However, the complex cells will responds to  an appropriately  oriented stimulus regardless of the cell position in the receptive field.
 Complex cells are activated by edge, dark bar, slit and mixed stimuli.
@@
 
-\par Hubel DH and Wiesel TN \cite{Hubel1965a} presented a functional hierarchical structure of the visual cortex.
-According to their model, visual perception cells are in the  order, simple$\Longrightarrow$ complex$\Longrightarrow$ lower order hypercomplex $\Longrightarrow$ higher  order hypercomplex.
+\par In the visual cortex, perception cells are in the  order,  simple$\Longrightarrow$ complex$\Longrightarrow$ lower order hypercomplex $\Longrightarrow$ higher  order hypercomplex.
 Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant.
@@
 It uses  local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance.
-A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al..\cite{LeCun1998}  for document recognition.
+A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al.\cite{LeCun1998}  for document recognition.
 Using local receptive fields network can extract elementary visual features such as edges, end point, and corners.
@@
 \emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between a input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
-. ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$. Where $b_j$ is a trainable bias , $i$ and $j$ are  array indices.\\
+. ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$. Where $b_j$ is a trainable bias , $i$ and $j$ are  array indices and $*$ is the convolution operator.\\
 \emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output.
@@
 \end{figure}
-
+But this architecture was limited by availability of the computing power and  sample data sets of that time. 
 %2012
@@
 One of the state-of-the-art error rate is from Krizhevsky, et al.\cite{Krizhevsky2012a}.
-Their network has 60 million parameters and 650,000 neurons, consists of five convolutional layers followed by max-pooling layers, and three fully-connected layers.
+It consist of 60 million parameters and 650,000 neurons, with five convolutional layers followed by max-pooling layers and three fully-connected layers.
 Data set used in this experiment was a subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{imagenet} and reported an error rate of 15.3\%.
-This data set includes 1.2 million images that contain 1,000 categories.
+ILSVRC data set includes 1.2 million images that contain 1,000 categories.
+This network uses rectifier  as the function in neurons.
+Even if it shows improvement in speed, this  ill-conditioned parameterization must be studied further to understand the effect in very large networks.
 
@@
 \cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network.
+Using multilayer perceptron instead of voting to approximate convex functions of each  local patches may result in a good accuracy, but this is equivalent to moving linear separability problem into another hyperspace.
+So if the input is in high frequency, this will end up modeling  large number of hidden layers and make the network structure more depend on the problem.
+It will diverge the idea  of the convolution network from  "learn anything" to a "local search".
 
@@
 This method helped  them  to understand  the activation in the feature maps with respect to the input patterns.
-It shows Krizhevsky et al..'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
-Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.
+It shows Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
+Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.Visualizations will help to debug the problem in some extend, But it become nearly impossible when there is large amount parameters involved.
+These  techniques may  more useful if it can relate to any of the learning formulations instead  vague  approximations of a non-invertible function.
 
@@
 However, the classical backpropagation training methods expect layers to have a fixed   size.
-To overcome this problem author implemented two fixed size networks with shared parameters and switched the network on alternate epochs.
-This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
+This problem can be solved  using two fixed size networks with shared parameters and switched the network on alternate epochs.
+Network was trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
 \par 
 This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}.
-Their study shows; accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations.
+Even if  the accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations, all this methods will increase both time and space complexity of the system.
 %

### 2015-01-28 paper/main.tex
draft v3

@@
 This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set.
-Their result shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
+This experiments shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
+Even if higher depth will increase the accuracy , this system will end up with implementing large number of hidden layers to increase accuracy for a high frequency input.
 
@@
 \par
- In this work authors formed a conclusion that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number  of epochs.
+It has been observed that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number  of epochs and also significant improvement in accuracy.
 This model of the convolution network does not differ from the classical architecture proposed by  LeCun et  al.
 \cite{LeCun1998}.
-But the authors reported a significant improvement in the performance using an increased depth.
 This implementation results in a significant improvement in accuracy with  an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.
@@
 System  uses an InfiniBand  network for interconnections.
-Parallelism strategies used in their network are model-data parallelism and data parallelism.
+Parallelism strategies used in this network are model-data parallelism and data parallelism.
 These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.
@@
 However, it is not easy extend the same strategies to multiple GPU clusters because of the communication overhead.
-So the  Baidu Team focused on minimizing network data transfers and overlapping the computation.
-They use butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation.
-Their results show model-data parallelism is better when number of GPUs is less than 16.
+So the  major objective is to minimize network data transfers and dynamic computation.
+So it uses butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation.
+This approaches  shows that model-data parallelism is better when number of GPUs is less than 16.
 Implementation of Data parallelism in a large number  of GPU  cluster is better because of the constant communication requirements.
 \par
-The authors have explored different data augmentation techniques to increase the number of labeled images in the training set.
+Data augmentation techniques  are used to increase the number of labeled images in the training set.
 This includes color casting, Vignetting, Lens distortion, Rotation, Flipping, and  Cropping.
-Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft-max class posteriors.
+Instead of using the same resolution on all images.
+Affine transformations on   the data set may increase the accuracy, But the major problems like occlusion, presence or absence of structural components, lighting conditions doesn't solve by applying simple augmentation techniques on the same data set.
+\begin{table*}[ht]
+ \begin{tabular}{ | p{3cm} | l | p{1.4cm} |p{1.3cm} |p{1cm} |p{1.2cm} |p{1.1cm} |p{6cm}|}
+    \hline
+Team	&Year	&Data Augmentation	&scalable over network	&Time taken	&Hardware	&Error on  ILSVRC & Observations
+\\ 
+\hline
+Ren Wu et al.\cite{Wu2015}	&2015	&aggressive	&Yes	&8.8 hours	&multi-GPU cluster	&5.98\% &Aggressive augmentation  will make the problem depend on data set\\
+\hline
+Karen Simonyan and Andrew Zisserman.\cite{Arge2015}	&2014	&minimum	&No	&3 weeks	&multi-GPU	&6.80\% &Effect of small convolution filter in low frequency domain need to be studied\\
+\hline
+Christian Szegedy and et al.\cite{Szegedy}	&2014	&minimum	&Yes	&more than a week	&CPU cluster	&6.67\% &Inserting more layers will make system depends on the data set \\
+\hline
+Kaiming He et al.\cite{He2014}	&2014	&minimum	&No	&4 weeks	&single GPU	&8.06\% &Good method, But higher time complexity\\
+\hline
+Matthew D. Zeiler and Rob Fergus \cite{Zeiler2013}	&2013	&minimum	&No	&12 days	&single GPU	&11.74\% & Visualizations are not possible in very deep network\\
+\hline
+Min Lin et al.\cite{Lin2013}	&2013	&minimum	&No	&Not reported	&single GPU	&12.95\% &Inserting more layers will over-fit the system \\
+\hline
+Krizhevsky, et al.\cite{Krizhevsky2012a}	&2012	&minimum	&No	&6 days	&multi-GPU	&15.30\% & Effect of rectifier must be studied further\\
+\hline
 
+\end{tabular}
+\caption[]{ Top 5 error rate in ILSVRC}
+\end{table*}
 \par
@@
  \end{subsection}
- \section {Summary}
+ \section {Observations}
+ After detailed analysis of the latest literature , we are listing some of the observations.
  \begin{enumerate}
 
- \item Wisely chosen data  augmentation techniques can increase the performance of the network.
- \item Data parallelism and model parallelism can increase the speed of the training process.
- \item Greater depth with small convolution filters will improve the accuracy.
+ \item Wisely chosen data  augmentation techniques can increase the performance of the network. But need to be tested with multiple data set.
+ \item Data parallelism and model parallelism can increase the speed of the training process. This area can be exploited further to increase the speed of the training process.
+ \item Greater depth with small convolution filters will improve the accuracy. But response to different frequency input must be studied .
  \item Network will get benefited from   image  in different scale .
@@
  \end{enumerate}
-
- \begin{table}[h]
- \begin{tabular}{ | p{5cm} | l | l |}
-    \hline
-Team	&Year	&Top 5 error\\
-    \hline
-        \hline
-Ren Wu et al.\cite{Wu2015}	&2015	&5.98\%\\
-    \hline
-Karen Simonyan and Andrew Zisserman.\cite{Arge2015}	&2014	&6.80\%\\
-    \hline
-Christian Szegedy and et al.\cite{Szegedy}	&2014	&6.67\%\\
-    \hline
-Kaiming He et al.\cite{He2014}	&2014	&8.06\%\\
-    \hline
-Matthew D. Zeiler and Rob Fergus \cite{Zeiler2013}	&2013	&11.74\%\\
-    \hline
-Min Lin et al.\cite{Lin2013}	&2013	&12.95\%\\
-    \hline
-Krizhevsky, et al.\cite{Krizhevsky2012a}	&2012	&15.30\%\\
-    \hline
-
-\end{tabular}
-\caption[]{ Top 5 error rate in ILSVRC}
-\end{table}
 

### 2015-01-29 paper/main (copy).tex
final , withot format

% Template for ICIP-2015 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}

\usepackage{spconf,amsmath,graphicx}
\usepackage{caption}
\usepackage{showframe}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title { On Deep Convolutional networks for large scale image classification}
%
% Single address.
% ---------------
\name{Mahesh C., Student Member, IEEE, Madhu S. Nair, Member, IEEE}
\address{Department of Computer Science, University of Kerala, Kariavattom\\ Thiruvananthapuram-695581,
	Kerala, India.
}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%

\begin{document}
\topmargin=0mm 
%\ninept
%
\maketitle
%
\begin{abstract}
Image classification is an essential to the field of computer vision  based systems and recent research in this area explores better feature extraction, feature coding, and classification.  The purpose of this paper is to review the application of supervised  deep convolution networks in this field. Numerous techniques have been reported to improve the performance of the convolution networks. Experimental analysis shows that with a large amount of labeled data, convolution networks can learn very complex functions such as image classification.

\end{abstract}
%
\begin{keywords}
convolution networks, deep learning, neural networks.
\end{keywords}
%
\section{Introduction}
\label{sec:intro}
The performance of an  image  classification system mainly depends on the  extraction and  representation of features.  Feature representation methods like Haralick texture features \cite{Haralick1973} got attention from the research community from the earlier days of  image classification. However, to develop features that are invariant to position, rotation, scaling, and distortion, researchers had  to  explore the visual perception of primates. This research  led to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}. 
As a result, many successful image classification systems are  implemented with better accuracy \cite{lecun-89e}.

Early in that stage, method like the convolutional network is limited by the  availability of labeled  data and computing infrastructure. Researchers are trying to overcome  this problem by many other non-parametric models such as SVM and KNN. But these methods couldn't give a high accuracy result  on any of the large-scale classification problem  and limited by the preprocessing technique.  However, in the recent years, the development of  High Performance Computing (HPC) architecture such as General Purpose Graphical Processing Units (GPGPU)  accelerated the research in this field. Large scale image  dataset such as ImageNet \cite{imagenet}  with  millions of labeled samples is also accessible to the research community. These changes in data and computing, put back the convolution network with millions of parameters in track.

\section{Multi-stage Hubel-Wiesel architecture}
In 1962, Hubel DH and Wiesel TN \cite{Hubel1962}, \cite{Hubel1965a}  studied visual cortex of anesthetized cats  with   spots of white light of various shapes. Cells in the visual system are classified    into  simple, complex and hypercomplex. Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field as well as the position of the stimulus. This cell receives input from cells of the lateral geniculate nucleus (LGN), which is connected to the retina. However, the complex cells will respond to  an appropriately  oriented stimulus regardless of the cell position in the receptive field. Complex cells are activated by edge, dark bar, slit and mixed stimuli. Hypercomplex cells are activated by edge, single-stopped (corner), double-stopped (tongue), slit (double-stopped) and dark bar (double-stopped).

\par In the visual cortex, perception cells are in the  order, simple$\Longrightarrow$complex$\Longrightarrow$lower-order-hypercomplex$\Longrightarrow$higher-order-hypercomplex. Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant. There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
\par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
In neocognitron, cells are arranged in  a number of  cascaded structure. Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$. This network is not affected by change in position or small distortion in the shape of patterns.  It is also capable of doing self-organization based on an unsupervised competitive learning algorithm \cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
\begin{figure}[ht]
 \centering
 \includegraphics[width=8cm]{Figures/neocognitron.eps}
\caption{Neocognitron}
\label{neo}
\end{figure}
\section{Convolutional Networks}
\par Neocognitron was improved by  Yann LeCun \cite{lecun-86}, \cite{lecun-89e}, using backpropagation algorithm  to train the entire system. It uses local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance. A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al. \cite{LeCun1998}  for document recognition. Using \allowbreak local receptive fields, network can extract elementary visual features such as edges, end points and corners. These features will be combined to obtain high order features in the following layers. Elementary feature detectors with identical weights can be useful in different parts of the image. So the units with  the same set of weights are arranged in plane, and output from  the units of a plane is called  a feature map. Units in  a feature map perform the same operation on different parts of the same image. A convolution layer is composed of the set of feature maps with differently weighed units. In the implementation, a unit in the feature map scans the image and store the states in the feature map. This operation is equivalent to convolution with a kernel composed of a  set of weights and image.

\par
A typical convolutional  network is composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
\begin{figure}[ht]

 \includegraphics[width=8cm]{Figures/convent.eps}
\caption{A typical convolutional network architecture }
\label{net}
\end{figure}
\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between an input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
 ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$, where $b_j$ is a trainable bias, $i$ and $j$ are  array indices, and $*$ is the convolution operator.\\
\emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output. But to reduce training time with gradient descent, new implementations uses the function $max(0,x)$. Units with this non-linearity is called Rectified Linear Units (ReLUs) \cite{Nair2010}.\\
\emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.

% -------------------------------------------------------------------------
\begin{figure}[t]

\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/org}}
%  \vspace{2.0cm}
  \centerline{Input image}\medskip
\end{minipage}
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/first}}
%  \vspace{1.5cm}
  \centerline{Output - first component }\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/second}}
%  \vspace{1.5cm}
  \centerline{Output - second component}\medskip
\end{minipage}
%
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/third}}
%  \vspace{1.5cm}
  \centerline{Output - third component}\medskip
\end{minipage}
%
\caption{Output of a randomly initialized convolution filter.
}
\label{fig:res}
%
\end{figure}

But this architecture was limited by the availability of computing power and  sample data sets. 
%2012

\section {Deep convolutional networks}
In the last few years, convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST \cite{Ciresan:2012g}, CIFAR-10, CIFAR-100, SVHN \cite{lee2014deeply}, and STL-10 \cite{deepfwd}. Krizhevsky, et al. \cite{Krizhevsky2012a} proposed a network  of 60 million parameters and 650,000 neurons, with five convolutional layers followed by max-pooling layers and three fully-connected layers. Data set used in this experiment was a subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC) \cite{imagenet} and reported an error rate of 15.3\%. ILSVRC data set includes 1.2 million images that contain 1,000 categories. This network uses rectifier  as the function in neurons.  Even if it shows improvement in speed, this  ill-conditioned parameterization must be studied further to understand the effect in very large networks.

%2013

\subsection{Network in Network }
Inspired by the work of Ian J. Goodfellow et al..\cite{Goodfellow2013} on max out networks,  Min Lin et al. \cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network. Using multilayer perceptron instead of voting to approximate convex functions of each  local patches may result in a good accuracy; but this is equivalent to moving linear separability problem into another hyperspace. So, if the input is in high frequency, this will end up in modeling large number of hidden layers and make the network structure more dependent on the problem. It will diverge the idea of the convolution network from \emph{learn anything} to a \emph{local search}.

\subsection{Visualizing Convolutional Networks}

Matthew D. Zeiler and Rob Fergus \cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of convolutional networks and used it as a diagnostic tool to improve  the model proposed by Krizhevsky et al. \cite{Krizhevsky2012a}. This method helped  them  to understand  the activation in the feature maps with respect to the input patterns. It shows that Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and causes aliasing artifacts by large stride in the first layer convolutions. Authors solved this problem by decreasing filter size to $7\times7$ and reducing stride to 2. This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%. These  techniques might be more useful if it can relate to any of the learning formulations instead of vague approximations of a non-invertible function.

%2014

\subsection{Spatial Pyramid Pooling in Deep Convolutional Networks}
Instead of using fixed input size in convolutional networks, Kaiming He et al. \cite{He2014} suggested  the use of a spooling strategy called  Spatial Pyramid Pooling (SPP) \cite{Grauman2005} \cite{1641019} to avoid cropping or warping of images. It introduced a new layer on top of the convolution layer and performed aggregation  based on Bag-of-Words (BoW) model. However, the classical backpropagation training methods expect layers to have a fixed   size.  This problem can be solved by using two fixed size networks with shared parameters and switch the network on alternate epochs. Network was trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set. 
\par 
This implementation improves the performance of baseline architectures including ZF-5 \cite{Zeiler2013}, Convnet \cite{Krizhevsky2012a} and Overfeat-5/7. Even if  the accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations, all these methods will increase both time and space complexity of the system.
%

\subsection{Going deeper with convolutions }
Christian Szegedy et al. \cite{Szegedy} proposed a network named GoogLeNet with receptive field (input layer) of size $244\times244$ with the number of layers around 100. Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on the number of epochs. Learning procedure took advantage of  model and data-parallelism in a CPU-based cluster environment. This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set. The experimental analysis shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks. Even if higher depth will increase the accuracy, this system will end up with implementing large number of hidden layers to increase accuracy for a high frequency input.

\section{VERY DEEP CONVOLUTIONAL NETWORKS }
Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters. Their deep network architecture comprised of fixed  size input layers, a stack of convolution layers, three Fully-Connected (FC) layers and  5 max-pooling layers for spatial pooling  over a $2 \times 2$ pixel window with stride 2. Hidden layers are modeled using Rectified Linear Units (ReLU) \cite{Nair2010}. On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs. Network is trained using multinomial logistic regression  based on backpropagation with momentum of 0.9 and  batch size  256.
\par
It has been observed that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number of epochs and gain significant improvement in accuracy. This model of the convolution network does not differ from the classical architecture proposed by LeCun et al. \cite{LeCun1998}. This implementation results in a significant improvement in accuracy with  an error rate of 6.8\% in ILSVRC 2014 of ImageNet.

\begin{subsection}{Scaling up Image Classification}
The latest attempt in image classification with an error rate of 5.98\% in ImageNet data set is reported by Ren Wu et al. \cite{Wu2015} of Baidu research. They developed an end to end deep learning  system named Deep Image. It uses a highly optimized parallel algorithm to implement large deep neural network with augmented input data. The network is trained using Stochastic Gradient Descent algorithms (SGD) on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs. System  uses an InfiniBand  network for interconnections. Parallelism strategies used in this network are model-data parallelism and data parallelism. These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al. \cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems. However, it is not easy to extend the same strategies to multiple GPU clusters because of the communication overhead. The major objective is to minimize network data transfers and dynamic computation. So it uses butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation. These approaches shows that model-data parallelism is better when number of GPUs is less than 16. Implementation of Data parallelism in a large number of GPU cluster is better because of the constant communication requirements.
\par
Data augmentation techniques are used to increase the number of labeled images in the training set. This includes color casting, vignetting, lens distortion, rotation, flipping and cropping. But this data augmentation techniques  doesn't solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
\centering
\begin{table*}[ht]
\captionsetup{justification=centering,belowskip=2pt,aboveskip=2pt}
\caption[]{ Comparative analysis of state-of-the-art deep convolutional network based image classification algorithms using ILSVRC dataset.}
 \begin{tabular}{ | p{2.7cm} | l | p{1.4cm} |p{1.3cm} |p{.8cm} |p{1.3cm} |p{1.1cm} |p{5cm}|}

    \hline
\textbf{Team}	&\textbf{Year}	&\textbf{Data Augmentation}	&\textbf{Scalable over network}	&\textbf{Time taken}	&\textbf{Hardware}	&\textbf{Error rate} &\textbf{Observations}
\\ 
\hline
Ren Wu et al. \cite{Wu2015}&2015&Aggressive&Yes&8.8 hours&Multi-GPU Cluster&5.98\%&Aggressive augmentation  will make the problem dependent on data set.\\
\hline
Karen Simonyan et al. \cite{Arge2015}&2014&Minimum&No&3 weeks&Multi-GPU&6.80\% &Effect of small convolution filter in low frequency domain need to be studied.\\
\hline
Christian Szegedy et al. \cite{Szegedy}&2014&Minimum&Yes&1 week&CPU Cluster&6.67\% &Inserting more layers will make system depend on the data set.\\
\hline
Kaiming He et al. \cite{He2014}&2014&Minimum&No&4 weeks	&Single GPU	&8.06\% &Good method, but higher time complexity.\\
\hline
Matthew D. Zeiler et al. \cite{Zeiler2013}&2013&Minimum&No&12 days&Single GPU&11.74\% & Visualizations are not possible in very deep network.\\
\hline
Min Lin et al. \cite{Lin2013}&2013&Minimum&No&12 days&Single GPU&12.95\% &Inserting more layers will over-fit the system.\\
\hline
Krizhevsky, et al.\cite{Krizhevsky2012a}&2012&Minimum&No&6 days	&Multi-GPU&15.30\%&Effect of rectifier must be studied further.\\
\hline

\end{tabular}
\label{table_cp}
\end{table*}
\par
 Major contribution of this work is the demonstration of tremendous computational power required to  achieve high accuracy in image classification.
It also shows that augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
 \end{subsection}
 \section {Observations}
In recent years, the research community has reported several image classification algorithms based on deep convolutional network which gives less rate. A comparative analysis of recent futuristic deep convolutional networks is shown in Table \ref{table_cp}.
  Ren Wu et al. \cite{Wu2015} uses aggressive data argumentation and high computational power to reduce the computational time and error rate. Karen Simonyan et al. \cite{Arge2015} work shows, error rate can be reduced using small convolution filters. Christian Szegedy  et al. \cite{Szegedy} and Min Lin et al. \cite{Lin2013} introduces a set of hidden layers to model local patches. Kaiming He et al. \cite{He2014} uses a different pooling technique to reduce the error rate. Krizhevsky, et al. \cite{Krizhevsky2012a}  introduces  rectifier  as the neuron function. Although significant progress has been made in the last few years, there is still room for further research and improvement. Major observations from our study are listed below.
 \begin{itemize}
 \itemsep0em 
 \item  Wisely chosen data  augmentation techniques can increase the performance of the network. But need to be tested with multiple data set.
 \item Data parallelism and model parallelism can increase the speed of the training process. This area can be exploited further to increase the speed of the training process.
 \item Greater depth with small convolution filters will improve the accuracy. But, response to different frequency input must be studied.
 \item Performance of the network will get improved if images at difference scales are used for training.
 \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural level may reduce the error rate. 
 \item Rectified Linear Units can increase the speed of SGD.

 \end{itemize}

\section{conclusion}
This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance. Majority of the reviewed  works are reported from ImageNet Large-Scale Visual Recognition Challenge. These networks can only be trained using very expensive computing resources such as multiGPU cluster  to achieve more accuracy on large data sets. So  this research heavily depends on other research domains such as parallel algorithms, computer networks and multicore architecture. Because of the heavy computational requirements, it is not easy to apply this method directly  to the small level computing platforms such as embedded systems and application level  processors. On the other side, these methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.

\bibliographystyle{IEEEbib}
\bibliography{survey}

\end{document}

### 2015-01-29 paper/main.tex
final , withot format

--- 2015-01-25 paper/main.tex
@@
 % --------------------------------------------------------------------------
-\documentclass{article}
+\documentclass[a4paper]{article}
+
 \usepackage{spconf,amsmath,graphicx}
+\usepackage{caption}
+\usepackage{showframe}
 
@@
 % ------
-\title { Deep Convolutional networks for large scale image classification - A Survey  }
+\title { On Deep Convolutional networks for large scale image classification}
 %
@@
 % ---------------
-\name{Author(s) Name(s)}
-\address{Author Affiliation(s)}
+\name{Mahesh C., Student Member, IEEE, Madhu S. Nair, Member, IEEE}
+\address{Department of Computer Science, University of Kerala, Kariavattom\\ Thiruvananthapuram-695581,
+	Kerala, India.
+}
 %
@@
 %
+
 \begin{document}
+\topmargin=0mm 
 %\ninept
@@
 Numerous techniques have been reported to improve the performance of the convolution networks.
-It has been shown that with a large amount of labeled data, convolution networks can learn very complex functions such as image classification and speech recognition.
+Experimental analysis shows that with a large amount of labeled data, convolution networks can learn very complex functions such as image classification.
 
@@
 \begin{keywords}
-convolution networks, deep learning , neural networks.
+convolution networks, deep learning, neural networks.
 \end{keywords}
@@
 Feature representation methods like Haralick texture features \cite{Haralick1973} got attention from the research community from the earlier days of  image classification.
-However, to develop features that are invariant to position, rotation, sailing, and distortion, researchers had  to  explore the visual perception of primates.
-This research  leads to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}.
+However, to develop features that are invariant to position, rotation, scaling, and distortion, researchers had  to  explore the visual perception of primates.
+This research  led to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}.
 As a result, many successful image classification systems are  implemented with better accuracy \cite{lecun-89e}.
@@
 Early in that stage, method like the convolutional network is limited by the  availability of labeled  data and computing infrastructure.
-However, in the recent years, the development of  High performance computing architecture such as general purpose graphical processing units (GPGPU )  accelerated the research in this field.
-Large scale image  dataset such as ImageNet\cite{imagenet}  with  millions of labeled samples is also accessible to the research community.
-This changes in data and computing, put back the convolution network with million of parameters in track.
+Researchers are trying to overcome  this problem by many other non-parametric models such as SVM and KNN.
+But these methods couldn't give a high accuracy result  on any of the large-scale classification problem  and limited by the preprocessing technique.
+However, in the recent years, the development of  High Performance Computing (HPC) architecture such as General Purpose Graphical Processing Units (GPGPU)  accelerated the research in this field.
+Large scale image  dataset such as ImageNet \cite{imagenet}  with  millions of labeled samples is also accessible to the research community.
+These changes in data and computing, put back the convolution network with millions of parameters in track.
 
 \section{Multi-stage Hubel-Wiesel architecture}
-In 1962, Hubel DH and Wiesel TN\cite{Hubel1962},\cite{Hubel1965a} was studied visual cortex of anesthetized cats  with   spots of white light of various shapes.
-They classified the  cells in the visual system into  simple, complex and hypercomplex.
-Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field, and  position of the stimulus is important.
-This cell receives input from cells of the lateral geniculate nucleus(LGN), which is connected to the retina.
-However, the complex cells will responds to  a properly  oriented stimulus regardless of the cell position in the receptive field.
+In 1962, Hubel DH and Wiesel TN \cite{Hubel1962}, \cite{Hubel1965a}  studied visual cortex of anesthetized cats  with   spots of white light of various shapes.
+Cells in the visual system are classified    into  simple, complex and hypercomplex.
+Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field as well as the position of the stimulus.
+This cell receives input from cells of the lateral geniculate nucleus (LGN), which is connected to the retina.
+However, the complex cells will respond to  an appropriately  oriented stimulus regardless of the cell position in the receptive field.
 Complex cells are activated by edge, dark bar, slit and mixed stimuli.
-Hypercomplex cells are activated by edge,single-stopped(corner),double-stopped (tongue),slit(double-stopped)and dark bar(double-stopped).
+Hypercomplex cells are activated by edge, single-stopped (corner), double-stopped (tongue), slit (double-stopped) and dark bar (double-stopped).
 
-\par Hubel DH and Wiesel TN \cite{Hubel1965a} presented a functional hierarchical structure of the visual cortex.
-According to their model, visual perception cells are in the  order, simple$\Longrightarrow$ complex$\Longrightarrow$ lower order hypercomplex $\Longrightarrow$ higher  order hypercomplex.
+\par In the visual cortex, perception cells are in the  order, simple$\Longrightarrow$complex$\Longrightarrow$lower-order-hypercomplex$\Longrightarrow$higher-order-hypercomplex.
 Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant.
@@
 \par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
-In neocognitron , cells are arranged in  a number of  cascaded structure.
+In neocognitron, cells are arranged in  a number of  cascaded structure.
 Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$.
 This network is not affected by change in position or small distortion in the shape of patterns.
-It is also capable of doing self-organization based on an unsupervised competitive learning algorithm\cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
+It is also capable of doing self-organization based on an unsupervised competitive learning algorithm \cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
 \begin{figure}[ht]
  \centering
- \includegraphics[width=9cm]{Figures/neocognitron.eps}
-\caption{Neocognitron\cite{Stark1980}}
+ \includegraphics[width=8cm]{Figures/neocognitron.eps}
+\caption{Neocognitron}
 \label{neo}
@@
 \section{Convolutional Networks}
-\par Neocognitron was improved by  Yann LeCun \cite{lecun-86},\cite{lecun-89d}, \cite{lecun-89e},\cite{lecun-90c}, \cite{lecun-90e} using backpropagation algorithm\cite{BRYSON1963} to train the entire system.
+\par Neocognitron was improved by  Yann LeCun \cite{lecun-86}, \cite{lecun-89e}, using backpropagation algorithm  to train the entire system.
 It uses local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance.
-A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al..\cite{LeCun1998}  for document recognition.
-Using local receptive fields network can extract elementary visual features such as edges, end point, and corners.
-This features will combine to obtain high order features in the following layers.
+A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al.
+\cite{LeCun1998}  for document recognition.
+Using \allowbreak local receptive fields, network can extract elementary visual features such as edges, end points and corners.
+These features will be combined to obtain high order features in the following layers.
 Elementary feature detectors with identical weights can be useful in different parts of the image.
-So the units with  the same set of weights are arranged in plane and output from  the units of a plane is called  a feature map.
+So the units with  the same set of weights are arranged in plane, and output from  the units of a plane is called  a feature map.
 Units in  a feature map perform the same operation on different parts of the same image.
@@
 \par
-A typical convolutional  network composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
+A typical convolutional  network is composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
 \begin{figure}[ht]
- \includegraphics[width=9.5cm]{Figures/convent.eps}
-\caption{A typical ConvNet architecture \cite{lecun2010convolutional}}
+
+ \includegraphics[width=8cm]{Figures/convent.eps}
+\caption{A typical convolutional network architecture }
 \label{net}
 \end{figure}
-\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between a input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
-. ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$. Where $b_j$ is a trainable bias , $i$ and $j$ are  array indices.\\
+\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between an input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
+ ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$, where $b_j$ is a trainable bias, $i$ and $j$ are  array indices, and $*$ is the convolution operator.\\
 \emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output.
-But to reduce training time with gradient decent, new implementations uses the function $max(0,x)$.
-Units with this non-linearity is called Rectified Linear Units (ReLUs)\cite{Nair2010}.\\
+But to reduce training time with gradient descent, new implementations uses the function $max(0,x)$.
+Units with this non-linearity is called Rectified Linear Units (ReLUs) \cite{Nair2010}.\\
 \emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
-\begin{figure}[ht]
+
+% -------------------------------------------------------------------------
+\begin{figure}[t]
+
+\begin{minipage}[b]{.48\linewidth}
   \centering
- \includegraphics[width=8cm]{Figures/conv.eps}
-\caption{Output of  a randomly initialized   convolution filter. Input image courtesy:dcsku.org}
-\label{conv}
+  \centerline{\includegraphics[width=4.0cm]{Figures/org}}
+%  \vspace{2.0cm}
+  \centerline{Input image}\medskip
+\end{minipage}
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{Figures/first}}
+%  \vspace{1.5cm}
+  \centerline{Output - first component }\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{Figures/second}}
+%  \vspace{1.5cm}
+  \centerline{Output - second component}\medskip
+\end{minipage}
+%
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{Figures/third}}
+%  \vspace{1.5cm}
+  \centerline{Output - third component}\medskip
+\end{minipage}
+%
+\caption{Output of a randomly initialized convolution filter.
+}
+\label{fig:res}
+%
 \end{figure}
 
+But this architecture was limited by the availability of computing power and  sample data sets. 
 %2012
@@
 \section {Deep convolutional networks}
-In last few years convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST\cite{Ciresan:2012g},CIFAR-10,CIFAR-100,SVHN\cite{lee2014deeply},STL-10 \cite{deepfwd}.
-One of the state-of-the-art error rate is from Krizhevsky, et al.\cite{Krizhevsky2012a}.
-Their network has 60 million parameters and 650,000 neurons, consists of five convolutional layers followed by max-pooling layers, and three fully-connected layers.
-Data set used in this experiment was a subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{imagenet} and reported an error rate of 15.3\%.
-This data set includes 1.2 million images that contain 1,000 categories.
+In the last few years, convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST \cite{Ciresan:2012g}, CIFAR-10, CIFAR-100, SVHN \cite{lee2014deeply}, and STL-10 \cite{deepfwd}.
+Krizhevsky, et al.
+\cite{Krizhevsky2012a} proposed a network  of 60 million parameters and 650,000 neurons, with five convolutional layers followed by max-pooling layers and three fully-connected layers.
+Data set used in this experiment was a subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC) \cite{imagenet} and reported an error rate of 15.3\%.
+ILSVRC data set includes 1.2 million images that contain 1,000 categories.
+This network uses rectifier  as the function in neurons.
+Even if it shows improvement in speed, this  ill-conditioned parameterization must be studied further to understand the effect in very large networks.
 
@@
 
-\subsection{Network In Network }
+\subsection{Network in Network }
 Inspired by the work of Ian J.
@@
 \cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network.
+Using multilayer perceptron instead of voting to approximate convex functions of each  local patches may result in a good accuracy; but this is equivalent to moving linear separability problem into another hyperspace.
+So, if the input is in high frequency, this will end up in modeling large number of hidden layers and make the network structure more dependent on the problem.
+It will diverge the idea of the convolution network from \emph{learn anything} to a \emph{local search}.
 
@@
 Matthew D.
-Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of convolutional networks and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al.
+Zeiler and Rob Fergus \cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of convolutional networks and used it as a diagnostic tool to improve  the model proposed by Krizhevsky et al.
 \cite{Krizhevsky2012a}.
 This method helped  them  to understand  the activation in the feature maps with respect to the input patterns.
-It shows Krizhevsky et al..'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions.
-Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.
+It shows that Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and causes aliasing artifacts by large stride in the first layer convolutions.
+Authors solved this problem by decreasing filter size to $7\times7$ and reducing stride to 2.
+This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.
+These  techniques might be more useful if it can relate to any of the learning formulations instead of vague approximations of a non-invertible function.
 
@@
 
-\subsection{Spatial pyramid pooling in Deep Convolutional Networks}
+\subsection{Spatial Pyramid Pooling in Deep Convolutional Networks}
 Instead of using fixed input size in convolutional networks, Kaiming He et al.
-\cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images.
-It introduced a new layer on top of the convolution layer and perform aggregation  based on Bag-of-Words (BoW) model \cite{Sivic2003}.
+\cite{He2014} suggested  the use of a spooling strategy called  Spatial Pyramid Pooling (SPP) \cite{Grauman2005} \cite{1641019} to avoid cropping or warping of images.
+It introduced a new layer on top of the convolution layer and performed aggregation  based on Bag-of-Words (BoW) model.
 However, the classical backpropagation training methods expect layers to have a fixed   size.
-To overcome this problem author implemented two fixed size networks with shared parameters and switched the network on alternate epochs.
-This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
+This problem can be solved by using two fixed size networks with shared parameters and switch the network on alternate epochs.
+Network was trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
 \par 
-This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}.
-Their study shows; accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations.
+This implementation improves the performance of baseline architectures including ZF-5 \cite{Zeiler2013}, Convnet \cite{Krizhevsky2012a} and Overfeat-5/7.
+Even if  the accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations, all these methods will increase both time and space complexity of the system.
 %
@@
 \subsection{Going deeper with convolutions }
-Christian Szegedy and et al.
-\cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100.
-Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs
-.
+Christian Szegedy et al.
+\cite{Szegedy} proposed a network named GoogLeNet with receptive field (input layer) of size $244\times244$ with the number of layers around 100.
+Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on the number of epochs.
 Learning procedure took advantage of  model and data-parallelism in a CPU-based cluster environment.
 This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set.
-Their result shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
+The experimental analysis shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
+Even if higher depth will increase the accuracy, this system will end up with implementing large number of hidden layers to increase accuracy for a high frequency input.
 
@@
 Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
-Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 \times 2$ pixel window with stride 2.
-Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}.
+Their deep network architecture comprised of fixed  size input layers, a stack of convolution layers, three Fully-Connected (FC) layers and  5 max-pooling layers for spatial pooling  over a $2 \times 2$ pixel window with stride 2.
+Hidden layers are modeled using Rectified Linear Units (ReLU) \cite{Nair2010}.
 On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs.
@@
 \par
- In this work authors formed a conclusion that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number  of epochs.
+It has been observed that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number of epochs and gain significant improvement in accuracy.
 This model of the convolution network does not differ from the classical architecture proposed by LeCun et al.
 \cite{LeCun1998}.
-But the authors reported a significant improvement in the performance using an increased depth.
 This implementation results in a significant improvement in accuracy with  an error rate of 6.8\% in ILSVRC 2014 of ImageNet.
@@
 \begin{subsection}{Scaling up Image Classification}
-The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al.
-\cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image.
+The latest attempt in image classification with an error rate of 5.98\% in ImageNet data set is reported by Ren Wu et al.
+\cite{Wu2015} of Baidu research.
+They developed an end to end deep learning  system named Deep Image.
 It uses a highly optimized parallel algorithm to implement large deep neural network with augmented input data.
-The network is trained using stochastic gradient decent algorithms (SGD on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs .
+The network is trained using Stochastic Gradient Descent algorithms (SGD) on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs.
 System  uses an InfiniBand  network for interconnections.
-Parallelism strategies used in their network are model-data parallelism and data parallelism.
+Parallelism strategies used in this network are model-data parallelism and data parallelism.
 These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.
 \cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems.
-However, it is not easy extend the same strategies to multiple GPU clusters because of the communication overhead.
-So the  Baidu Team focused on minimizing network data transfers and overlapping the computation.
-They use butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation.
-Their results show model-data parallelism is better when number of GPUs is less than 16.
+However, it is not easy to extend the same strategies to multiple GPU clusters because of the communication overhead.
+The major objective is to minimize network data transfers and dynamic computation.
+So it uses butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation.
+These approaches shows that model-data parallelism is better when number of GPUs is less than 16.
 Implementation of Data parallelism in a large number of GPU cluster is better because of the constant communication requirements.
 \par
-The authors have explored different data augmentation techniques to increase the number of labeled images in the training set.
-This includes color casting, Vignetting, Lens distortion, Rotation, Flipping, and  Cropping.
-Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft-max class posteriors.
+Data augmentation techniques are used to increase the number of labeled images in the training set.
+This includes color casting, vignetting, lens distortion, rotation, flipping and cropping.
+But this data augmentation techniques  doesn't solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
+\centering
+\begin{table*}[ht]
+\captionsetup{justification=centering,belowskip=2pt,aboveskip=2pt}
+\caption[]{ Comparative analysis of state-of-the-art deep convolutional network based image classification algorithms using ILSVRC dataset.}
+ \begin{tabular}{ | p{2.7cm} | l | p{1.4cm} |p{1.3cm} |p{.8cm} |p{1.3cm} |p{1.1cm} |p{5cm}|}
 
+    \hline
+\textbf{Team}	&\textbf{Year}	&\textbf{Data Augmentation}	&\textbf{Scalable over network}	&\textbf{Time taken}	&\textbf{Hardware}	&\textbf{Error rate} &\textbf{Observations}
+\\ 
+\hline
+Ren Wu et al. \cite{Wu2015}&2015&Aggressive&Yes&8.8 hours&Multi-GPU Cluster&5.98\%&Aggressive augmentation  will make the problem dependent on data set.\\
+\hline
+Karen Simonyan et al. \cite{Arge2015}&2014&Minimum&No&3 weeks&Multi-GPU&6.80\% &Effect of small convolution filter in low frequency domain need to be studied.\\
+\hline
+Christian Szegedy et al. \cite{Szegedy}&2014&Minimum&Yes&1 week&CPU Cluster&6.67\% &Inserting more layers will make system depend on the data set.\\
+\hline
+Kaiming He et al. \cite{He2014}&2014&Minimum&No&4 weeks	&Single GPU	&8.06\% &Good method, but higher time complexity.\\
+\hline
+Matthew D. Zeiler et al. \cite{Zeiler2013}&2013&Minimum&No&12 days&Single GPU&11.74\% & Visualizations are not possible in very deep network.\\
+\hline
+Min Lin et al. \cite{Lin2013}&2013&Minimum&No&12 days&Single GPU&12.95\% &Inserting more layers will over-fit the system.\\
+\hline
+Krizhevsky, et al.\cite{Krizhevsky2012a}&2012&Minimum&No&6 days	&Multi-GPU&15.30\%&Effect of rectifier must be studied further.\\
+\hline
+
+\end{tabular}
+\label{table_cp}
+\end{table*}
 \par
- Major contribution of this work is the demonstration of tremendous computational power to achieve high accuracy in image classification.
-It also shows augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
+ Major contribution of this work is the demonstration of tremendous computational power required to  achieve high accuracy in image classification.
+It also shows that augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
  \end{subsection}
- \section {Summary}
- \begin{enumerate}
-
- \item Wisely chosen data  augmentation techniques can increase the performance of the network.
- \item Data parallelism and model parallelism can increase the speed of the training process.
- \item Greater depth with small convolution filters will improve the accuracy.
- \item Network will get benefited from   image  in different scale .
+ \section {Observations}
+In recent years, the research community has reported several image classification algorithms based on deep convolutional network which gives less rate.
+A comparative analysis of recent futuristic deep convolutional networks is shown in Table \ref{table_cp}.
+  Ren Wu et al.
+\cite{Wu2015} uses aggressive data argumentation and high computational power to reduce the computational time and error rate.
+Karen Simonyan et al.
+\cite{Arge2015} work shows, error rate can be reduced using small convolution filters.
+Christian Szegedy  et al.
+\cite{Szegedy} and Min Lin et al.
+\cite{Lin2013} introduces a set of hidden layers to model local patches.
+Kaiming He et al.
+\cite{He2014} uses a different pooling technique to reduce the error rate.
+Krizhevsky, et al.
+\cite{Krizhevsky2012a}  introduces  rectifier  as the neuron function.
+Although significant progress has been made in the last few years, there is still room for further research and improvement.
+Major observations from our study are listed below.
+ \begin{itemize}
+ \itemsep0em 
+ \item  Wisely chosen data  augmentation techniques can increase the performance of the network. But need to be tested with multiple data set.
+ \item Data parallelism and model parallelism can increase the speed of the training process. This area can be exploited further to increase the speed of the training process.
+ \item Greater depth with small convolution filters will improve the accuracy. But, response to different frequency input must be studied.
+ \item Performance of the network will get improved if images at difference scales are used for training.
  \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural level may reduce the error rate. 
@@
 
- \end{enumerate}
-
- \begin{table}[h]
- \begin{tabular}{ | p{5cm} | l | l |}
-    \hline
-Team	&Year	&Top 5 error\\
-    \hline
-        \hline
-Ren Wu et al.\cite{Wu2015}	&2015	&5.98\%\\
-    \hline
-Karen Simonyan and Andrew Zisserman.\cite{Arge2015}	&2014	&6.80\%\\
-    \hline
-Christian Szegedy and et al.\cite{Szegedy}	&2014	&6.67\%\\
-    \hline
-Kaiming He et al.\cite{He2014}	&2014	&8.06\%\\
-    \hline
-Matthew D. Zeiler and Rob Fergus \cite{Zeiler2013}	&2013	&11.74\%\\
-    \hline
-Min Lin et al.\cite{Lin2013}	&2013	&12.95\%\\
-    \hline
-Krizhevsky, et al.\cite{Krizhevsky2012a}	&2012	&15.30\%\\
-    \hline
-
-\end{tabular}
-\caption[]{ Top 5 error rate in ILSVRC}
-\end{table}
+ \end{itemize}
 
@@
 This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance.
-Majority of the reviewed  works are reported from ImageNet Largqe-Scale Visual Recognition Challenge.
-There is no work exist to our knowledge, that explain all underpinning mathematics  of  deep convolutional  networks.
-This networks can only be trained using very expensive computing resources such as multiGPU cluster  to achieve more accuracy on large data sets.
+Majority of the reviewed  works are reported from ImageNet Large-Scale Visual Recognition Challenge.
+These networks can only be trained using very expensive computing resources such as multiGPU cluster  to achieve more accuracy on large data sets.
 So  this research heavily depends on other research domains such as parallel algorithms, computer networks and multicore architecture.
 Because of the heavy computational requirements, it is not easy to apply this method directly  to the small level computing platforms such as embedded systems and application level  processors.
-On the other side, this methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.
+On the other side, these methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.
 

### 2015-01-31 deep_conv_net_survey/main.tex
deep convolutinal network survey completed

--- 2015-01-29 paper/main (copy).tex
@@
 \usepackage{caption}
-\usepackage{showframe}
+
+%\textwidth=178mm  
+%\textheight=229mm
+%\marginparwidth=19mm 
+%\topmargin=35mm
+
+% Example definitions.
+% --------------------
+\def\x{{\mathbf x}}
+\def\L{{\cal L}}
+
+% Title.
+% ------
+\title { On Deep Convolutional networks for large scale image classification}
+%
+% Single address.
+% ---------------
+\name{Mahesh C., Student Member, IEEE, Madhu S. Nair, Member, IEEE}
+\address{Department of Computer Science, University of Kerala, Kariavattom\\ Thiruvananthapuram-695581,
+	Kerala, India.
+}
+%
+% For example:
+% ------------
+%\address{School\\
+%	Department\\
+%	Address}
+%
+% Two addresses (uncomment and modify for two-address case).
+% ----------------------------------------------------------
+%\twoauthors
+%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
+%	{School A-B\\
+%	Department A-B\\
+%	Address A-B}
+%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
+%	while at ...}}
+%	{School C-D\\
+%	Department C-D\\
+%	Address C-D}
+%
+
+\begin{document}
+\topmargin=0mm 
+%\ninept
+%
+\maketitle
+%
+\begin{abstract}
+Image classification is an essential to the field of computer vision  based systems and recent research in this area explores better feature extraction, feature coding, and classification.
+The purpose of this paper is to review the application of supervised  deep convolution networks in this field.
+Numerous techniques have been reported to improve the performance of the convolution networks.
+Experimental analysis shows that with a large amount of labeled data, convolution networks can learn very complex functions such as image classification.
+
+\end{abstract}
+%
+\begin{keywords}
+convolution networks, deep learning, neural networks.
+\end{keywords}
+%
+\section{Introduction}
+\label{sec:intro}
+The performance of an  image  classification system mainly depends on the  extraction and  representation of features.
+Feature representation methods like Haralick texture features \cite{Haralick1973} got attention from the research community from the earlier days of  image classification.
+However, to develop features that are invariant to position, rotation, scaling, and distortion, researchers had  to  explore the visual perception of primates.
+This research  led to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}.
+As a result, many successful image classification systems are  implemented with better accuracy \cite{lecun-89e}.
+
+Early in that stage, method like the convolutional network is limited by the  availability of labeled  data and computing infrastructure.
+Researchers are trying to overcome  this problem by many other non-parametric models such as SVM and KNN.
+But these methods couldn't give a high accuracy result  on any of the large-scale classification problem  and limited by the preprocessing technique.
+However, in the recent years, the development of  High Performance Computing (HPC) architecture such as General Purpose Graphical Processing Units (GPGPU)  accelerated the research in this field.
+Large scale image  dataset such as ImageNet \cite{imagenet}  with  millions of labeled samples is also accessible to the research community.
+These changes in data and computing, put back the convolution network with millions of parameters in track.
+
+\section{Multi-stage Hubel-Wiesel architecture}
+In 1962, Hubel DH and Wiesel TN \cite{Hubel1962}, \cite{Hubel1965a}  studied visual cortex of anesthetized cats  with   spots of white light of various shapes.
+Cells in the visual system are classified    into  simple, complex and hypercomplex.
+Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field as well as the position of the stimulus.
+This cell receives input from cells of the lateral geniculate nucleus (LGN), which is connected to the retina.
+However, the complex cells will respond to  an appropriately  oriented stimulus regardless of the cell position in the receptive field.
+Complex cells are activated by edge, dark bar, slit and mixed stimuli.
+Hypercomplex cells are activated by edge, single-stopped (corner), double-stopped (tongue), slit (double-stopped) and dark bar (double-stopped).
+
+\par In the visual cortex, perception cells are in the  order, simple$\Longrightarrow$complex$\Longrightarrow$lower-order-hypercomplex$\Longrightarrow$higher-order-hypercomplex.
+Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant.
+There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
+\par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
+In neocognitron, cells are arranged in  a number of  cascaded structure.
+Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$.
+This network is not affected by change in position or small distortion in the shape of patterns.
+It is also capable of doing self-organization based on an unsupervised competitive learning algorithm \cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8cm]{Figures/neocognitron.eps}
+ \captionsetup{justification=centering,belowskip=0pt,aboveskip=0pt}
+\caption{Neocognitron}
+\label{neo}
+\end{figure}
+\section{Convolutional Networks}
+\par Neocognitron was improved by  Yann LeCun \cite{lecun-86}, \cite{lecun-89e}, using backpropagation algorithm  to train the entire system.
+It uses local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance.
+A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al.
+\cite{LeCun1998}  for document recognition.
+Using \allowbreak local receptive fields, network can extract elementary visual features such as edges, end points and corners.
+These features will be combined to obtain high order features in the following layers.
+Elementary feature detectors with identical weights can be useful in different parts of the image.
+So the units with  the same set of weights are arranged in plane, and output from  the units of a plane is called  a feature map.
+Units in  a feature map perform the same operation on different parts of the same image.
+A convolution layer is composed of the set of feature maps with differently weighed units.
+In the implementation, a unit in the feature map scans the image and store the states in the feature map.
+This operation is equivalent to convolution with a kernel composed of a  set of weights and image.
+
+\par
+A typical convolutional  network is composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
+\begin{figure}[ht]
+
+ \includegraphics[width=7cm]{Figures/convent.eps}
+\caption{A typical convolutional network architecture }
+\label{net}
+\end{figure}
+\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between an input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
+ ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$, where $b_j$ is a trainable bias, $i$ and $j$ are  array indices, and $*$ is the convolution operator.\\
+\emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output.
+But to reduce training time with gradient descent, new implementations uses the function $max(0,x)$.
+Units with this non-linearity is called Rectified Linear Units (ReLUs) \cite{Nair2010}.\\
+\emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
+
+% -------------------------------------------------------------------------
+\begin{figure}[t]
+
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=3.8cm]{Figures/org}}
+%  \vspace{2.0cm}
+  \centerline{Input image}\medskip
+\end{minipage}
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=3.8cm]{Figures/first}}
+%  \vspace{1.5cm}
+  \centerline{Output - first component }\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=3.8cm]{Figures/second}}
+%  \vspace{1.5cm}
+  \centerline{Output - second component}\medskip
+\end{minipage}
+%
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=3.8cm]{Figures/third}}
+%  \vspace{1.5cm}
+  \centerline{Output - third component}\medskip
+\end{minipage}
+%
+\caption{Output of a randomly initialized convolution filter.
+}
+\label{fig:res}
+%
+\end{figure}
+
+But this architecture was limited by the availability of computing power and  sample data sets. 
+%2012
+
+\section {Deep convolutional networks}
+In the last few years, convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST \cite{Ciresan:2012g}, CIFAR-10, CIFAR-100, SVHN \cite{lee2014deeply}, and STL-10 \cite{deepfwd}.
+Krizhevsky, et al.
+\cite{Krizhevsky2012a} proposed a network  of 60 million parameters and 650,000 neurons, with five convolutional layers followed by max-pooling layers and three fully-connected layers.
+Data set used in this experiment was a subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC) \cite{imagenet} and reported an error rate of 15.3\%.
+ILSVRC data set includes 1.2 million images that contain 1,000 categories.
+This network uses rectifier  as the function in neurons.
+Even if it shows improvement in speed, this  ill-conditioned parameterization must be studied further to understand the effect in very large networks.
+
+%2013
+
+\subsection{Network in Network }
+Inspired by the work of Ian J.
+Goodfellow et al..\cite{Goodfellow2013} on max out networks,  Min Lin et al.
+\cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network.
+Using multilayer perceptron instead of voting to approximate convex functions of each  local patches may result in a good accuracy; but this is equivalent to moving linear separability problem into another hyperspace.
+So, if the input is in high frequency, this will end up in modeling large number of hidden layers and make the network structure more dependent on the problem.
+It will diverge the idea of the convolution network from \emph{learn anything} to a \emph{local search}.
+
+\subsection{Visualizing Convolutional Networks}
+
+Matthew D.
+Zeiler and Rob Fergus \cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of convolutional networks and used it as a diagnostic tool to improve  the model proposed by Krizhevsky et al.
+\cite{Krizhevsky2012a}.
+This method helped  them  to understand  the activation in the feature maps with respect to the input patterns.
+It shows that Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and causes aliasing artifacts by large stride in the first layer convolutions.
+Authors solved this problem by decreasing filter size to $7\times7$ and reducing stride to 2.
+This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.
+These  techniques might be more useful if it can relate to any of the learning formulations instead of vague approximations of a non-invertible function.
+
+%2014
+
+\subsection{Spatial Pyramid Pooling in Deep Convolutional Networks}
+Instead of using fixed input size in convolutional networks, Kaiming He et al.
+\cite{He2014} suggested  the use of a spooling strategy called  Spatial Pyramid Pooling (SPP) \cite{Grauman2005} \cite{1641019} to avoid cropping or warping of images.
+It introduced a new layer on top of the convolution layer and performed aggregation  based on Bag-of-Words (BoW) model.
+However, the classical backpropagation training methods expect layers to have a fixed   size.
+This problem can be solved by using two fixed size networks with shared parameters and switch the network on alternate epochs.
+Network was trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
+\par 
+This implementation improves the performance of baseline architectures including ZF-5 \cite{Zeiler2013}, Convnet \cite{Krizhevsky2012a} and Overfeat-5/7.
+Even if  the accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations, all these methods will increase both time and space complexity of the system.
+%
+
+\subsection{Going deeper with convolutions }
+Christian Szegedy et al.
+\cite{Szegedy} proposed a network named GoogLeNet with receptive field (input layer) of size $244\times244$ with the number of layers around 100.
+Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on the number of epochs.
+Learning procedure took advantage of  model and data-parallelism in a CPU-based cluster environment.
+This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set.
+The experimental analysis shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
+Even if higher depth will increase the accuracy, this system will end up with implementing large number of hidden layers to increase accuracy for a high frequency input.
+
+\section{VERY DEEP CONVOLUTIONAL NETWORKS }
+Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
+Their deep network architecture comprised of fixed  size input layers, a stack of convolution layers, three Fully-Connected (FC) layers and  5 max-pooling layers for spatial pooling  over a $2 \times 2$ pixel window with stride 2.
+Hidden layers are modeled using Rectified Linear Units (ReLU) \cite{Nair2010}.
+On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs.
+Network is trained using multinomial logistic regression  based on backpropagation with momentum of 0.9 and  batch size  256.
+\par
+It has been observed that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number of epochs and gain significant improvement in accuracy.
+This model of the convolution network does not differ from the classical architecture proposed by LeCun et al.
+\cite{LeCun1998}.
+This implementation results in a significant improvement in accuracy with  an error rate of 6.8\% in ILSVRC 2014 of ImageNet.
+
+\begin{subsection}{Scaling up Image Classification}
+The latest attempt in image classification with an error rate of 5.98\% in ImageNet data set is reported by Ren Wu et al.
+\cite{Wu2015} of Baidu research.
+They developed an end to end deep learning  system named Deep Image.
+It uses a highly optimized parallel algorithm to implement large deep neural network with augmented input data.
+The network is trained using Stochastic Gradient Descent algorithms (SGD) on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs.
+System  uses an InfiniBand  network for interconnections.
+Parallelism strategies used in this network are model-data parallelism and data parallelism.
+These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.
+\cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems.
+However, it is not easy to extend the same strategies to multiple GPU clusters because of the communication overhead.
+The major objective is to minimize network data transfers and dynamic computation.
+So it uses butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation.
+These approaches shows that model-data parallelism is better when number of GPUs is less than 16.
+%Implementation of Data parallelism in a large number of GPU cluster is better because of the constant communication requirements.
+\par
+Data augmentation techniques are used to increase the number of labeled images in the training set.
+This includes color casting, vignetting, lens distortion, rotation, flipping and cropping.
+But this data augmentation techniques  does not solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
+\centering
+\begin{table*}[ht]
+\captionsetup{justification=centering,belowskip=1pt,aboveskip=1pt}
+\caption[]{ Comparative analysis of state-of-the-art deep convolutional network based image classification algorithms using ILSVRC dataset.}
+ \begin{tabular}{ | p{2.7cm} | l | p{1.4cm} |p{1.1cm} |p{.8cm} |p{1.3cm} |p{1.1cm} |p{5cm}|}
+
+    \hline
+\textbf{Team}	&\textbf{Year}	&\textbf{Data Augmentation}	&\textbf{Scalable over network}	&\textbf{Time taken}	&\textbf{Hardware}	&\textbf{Error rate} &\textbf{Observations}
+\\ 
+\hline
+Ren Wu et al. \cite{Wu2015}&2015&Aggressive&Yes&8.8 hours&Multi-GPU Cluster&5.98\%&Aggressive augmentation  will make the problem dependent on data set.\\
+\hline
+Karen Simonyan et al. \cite{Arge2015}&2014&Minimum&No&3 weeks&Multi-GPU&6.80\% &Effect of small convolution filter in low frequency domain need to be studied.\\
+\hline
+Christian Szegedy et al. \cite{Szegedy}&2014&Minimum&Yes&1 week&CPU Cluster&6.67\% &Inserting more layers will make system depend on the data set.\\
+\hline
+Kaiming He et al. \cite{He2014}&2014&Minimum&No&4 weeks	&Single GPU	&8.06\% &Good method, but higher time complexity.\\
+\hline
+Matthew D. Zeiler et al. \cite{Zeiler2013}&2013&Minimum&No&12 days&Single GPU&11.74\% & Visualizations are not possible in very deep network.\\
+\hline
+Min Lin et al. \cite{Lin2013}&2013&Minimum&No&12 days&Single GPU&12.95\% &Inserting more layers will over-fit the system.\\
+\hline
+Krizhevsky, et al.\cite{Krizhevsky2012a}&2012&Minimum&No&6 days	&Multi-GPU&15.30\%&Effect of rectifier must be studied further.\\
+\hline
+
+\end{tabular}
+\label{table_cp}
+\end{table*}
+\par
+ Major contribution of this work is the demonstration of tremendous computational power required to  achieve high accuracy in image classification.
+It also shows that augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
+ \end{subsection}
+ \section {Observations}
+In recent years, the research community has reported several image classification algorithms based on deep convolutional network which gives less rate.
+A comparative analysis of recent futuristic deep convolutional networks is shown in Table \ref{table_cp}.
+  Ren Wu et al.
+\cite{Wu2015} uses aggressive data argumentation and high computational power to reduce the computational time and error rate.
+Karen Simonyan et al.
+\cite{Arge2015} work shows, error rate can be reduced using small convolution filters.
+Christian Szegedy  et al.
+\cite{Szegedy} and Min Lin et al.
+\cite{Lin2013} introduces a set of hidden layers to model local patches.
+Kaiming He et al.
+\cite{He2014} uses a different pooling technique to reduce the error rate.
+Krizhevsky, et al.
+\cite{Krizhevsky2012a}  introduces  rectifier  as the neuron function.
+Although significant progress has been made in the last few years, there is still room for further research and improvement.
+Major observations from our study are listed below.
+ \begin{itemize}
+ \itemsep0em 
+ \item  Wisely chosen data  augmentation techniques can increase the performance of the network. But need to be tested with multiple data set.
+ \item Data parallelism and model parallelism can increase the speed of the training process. This area can be exploited further to increase the speed of the training process.
+ \item Greater depth with small convolution filters will improve the accuracy. But, response to different frequency input must be studied.
+ \item Performance of the network will get improved if images at difference scales are used for training.
+ \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural level may reduce the error rate. 
+ \end{itemize}
+
+\section{conclusion}
+This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance.
+Majority of the reviewed  works are reported from ImageNet Large-Scale Visual Recognition Challenge.
+These networks can only be trained using very expensive computing resources such as multiGPU cluster  to achieve more accuracy on large data sets.
+So  this research heavily depends on other research domains such as parallel algorithms, computer networks and multicore architecture.
+Because of the heavy computational requirements, it is not easy to apply this method directly  to the small level computing platforms such as embedded systems and application level  processors.
+On the other side, these methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.
+
+\bibliographystyle{IEEEbib}
+\bibliography{refs}
+
+\end{document}% Template for ICIP-2015 paper; to be used with:
+%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
+%          IEEEbib.bst - IEEE bibliography style file.
+% --------------------------------------------------------------------------
+\documentclass{article}
+
+\usepackage{spconf,amsmath,graphicx}
+\usepackage{caption}
 
@@
 % -------------------------------------------------------------------------
+
 \begin{figure}[t]
@@
 %
+
 \caption{Output of a randomly initialized convolution filter.
@@
 This includes color casting, vignetting, lens distortion, rotation, flipping and cropping.
-But this data augmentation techniques  doesn't solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
-\centering
+But this data augmentation techniques does not solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
 \begin{table*}[ht]
-\captionsetup{justification=centering,belowskip=2pt,aboveskip=2pt}
+\captionsetup{justification=centering,belowskip=-2pt,aboveskip=-2pt}
 \caption[]{ Comparative analysis of state-of-the-art deep convolutional network based image classification algorithms using ILSVRC dataset.}
@@
  \begin{itemize}
- \itemsep0em 
+ \itemsep0pt 
  \item  Wisely chosen data  augmentation techniques can increase the performance of the network. But need to be tested with multiple data set.
@@
  \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural level may reduce the error rate. 
- \item Rectified Linear Units can increase the speed of SGD.
-
 \end{itemize}
-
 \section{conclusion}
@@
 \bibliographystyle{IEEEbib}
-\bibliography{survey}
+\bibliography{refs}
 

### 2015-03-16 vslam/av/survey.tex
started with brief

\documentclass{article}
\title{On Autonomous vehicles - Systems and Algorithms}
\author{Mahesh C\\University of Kerala}

\begin{document}
\maketitle
\section{Simultaneous Localization And Mapping(SLAM) }
Estimating the vehicle position and surrounding map  is a necessary condition to achieve autonomous driving. There are multiple sensors like LIDAR, RADAR, Inertial Measurement Unit(IMU), GPS and the stereo Camera are  used to obtain a surrounding map. A navigational map  is obtained by fusing the data from these  sensors.\\

\subsection{Generic Methods}
Following are the commonly used sensor fusion algorithms used in SLAM.\\

\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{4cm}|}
\hline
Algorithm	&Algorithm Type	&Computational Effort	&Theoritical base\\
\hline
Histogram Filters	&SLAM	&High	&Bayes\\
\hline
Particle Filters	&SLAM 	&Medium	&Bayesian recursion\\
\hline
Extended Kalman filters	&SLAM	&Medium	&Kalman Filters\\
\hline
Rao-Blackwellised Filter	&SLAM	&Minimum	&Reduce the sample-space by applying Rao-Blackwellisation (R-B)\\
\hline
Bundle adjustment	&Visual SLAM	&High	&predicted projection of points\\
\hline
\end{tabular}

\subsection{Visual SLAM(VSLAM)}
Instead of using high cost sensors such as LIDAR, VSLAM techniques uses camera as the basic sensor.
Following are the commonly used sensor fusion algorithms used in SLAM.\\
\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{4cm}|}
\hline
Algorithm	&Algorithm Type	&Computational Effort	&Theoritical base\\
\hline
Multi-frame Feature Integration	&Visual Odometry	&High	&Optical flow\\
\hline
TLBBA	&Visual Odometry	&High	&Stereo odometry\\
\hline
2FO-CC	&Visual Odometry	&High	&Correcting the Calibration Bias\\
\hline
VOFSLBA	&Visual Odometry	&High	&flow separation and local bundle adjustment\\
\hline
\end{tabular}

\section{Motion Planning}

Map obtained from a SLAM algorithm is used to plan the motion of the vehicle through the given GPS waypoints. Some of the algorithms used to  plan the motion of an autonomous vehicle is given below.\\

\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{3cm}|}
\hline
Algorithm	&Algorithm Type	&Computational Effort	&Theoritical base\\
\hline
A* 	&Search	&High	& Edsger Dijkstra's 1959 algorithm\\
\hline
D*	& Search	&High	& incremental search algorithm\\
\hline
Anytime Dynamic A*	&Search	&High	&A*\\
\hline
 Probabilistic roadmap	&Search	&High	&Random sampling\\
\hline

\end{tabular}

\section{Object detection, recognition and scene understanding}
Object recognition algorithms are used to understand the objects/obstacles  around the vehicle. The primary obstacle avoidance methods are based on the point clouds generated from the LIDAR and RADAR data.  But the object recognition methods are more rely on the visual sensors such as camera. Majority of the algorithms uses supervised  machine learning methods to recognize the object. Some of the widely used methods are listed below.\\

\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{3cm}|}
\hline
Algorithm	&Algorithm Type	&Computational Effort	&Theoritical base\\
\hline
Bayesian Classification 	&Classification	&High	&Bayes\\
\hline
Deep Convolution network	&Classification	&High	&neural networks\\
\hline
Support Vector Machine	&Classification	&High	&Kernel Tricks\\
\hline

\end{tabular}

\begin{thebibliography}{9}
\bibitem{mfi}Badino, Hernán, Akihiro Yamamoto, and Takeo Kanade. "Visual odometry by multi-frame feature integration." Computer Vision Workshops (ICCVW), 2013 IEEE International Conference on. IEEE, 2013.
\bibitem{tlbba}Lu, Wei, Zhiyu Xiang, and Jilin Liu. "High-performance visual odometry with two-stage local binocular ba and gpu." Intelligent Vehicles Symposium (IV), 2013 IEEE. IEEE, 2013.
\bibitem{flow}Kaess, Michael, Kai Ni, and Frank Dellaert. "Flow separation for fast and robust stereo odometry." Robotics and Automation, 2009. ICRA'09. IEEE International Conference on. IEEE, 2009.
\end{thebibliography}

\end{document}

### 2015-03-17 vslam/odometry/sae2015_digest.tex
added LIOP details

\documentclass{article}
\usepackage{setspace}
\usepackage[margin=1 in]{geometry}
\usepackage{amsmath,graphicx}
\author{\#Authors}
\title{Stereo odometry based on  Local Intensity Order Pattern}
\doublespacing
\begin{document}
\maketitle
\begin{abstract}
New generation autonomous vehicles use different data fusion techniques to solve the Simultaneous Localization And Mapping (SLAM) problems in urban terrains.  However, the majority of the implementations uses high-cost sensors like LIDAR to obtain a high accuracy map. In this paper, we  present a novel method  to solve this problem using sequences of stereo images. Our approach uses Local Intensity Order Pattern (LIOP) based  feature descriptors to  overcome the problem of monotonic intensity changes and affine transformations of detected features. Egomotion of the vehicle is estimated using correspondence of features on the consecutive frames. Estimated motion parameters are then corrected using an extended Kalman filter. Depth of the detected features is calculated using stereo triangulation. Mahalanobis distance  is used to avoid outliers in the detected features.
The accuracy of  the proposed method is  evaluated using the measurements from a  high accurate inertial navigation system. Method is tested using the odometry data set of the KITTI Vision Benchmark Suite.

\end{abstract}
\section{Local Intensity Order Pattern Descriptor}
The performance of a visual odometry system  depends on extraction and representation of features. To achieve a consistent odometry in adverse weather and lighting conditions, the descriptor must be invariant to  photometric transforms such as  specular reflections, complex illumination changes and monotonic intensity changes.
However, the widely used descriptors such as Scale Invariant Feature Transform(SIFT) and Gradient Location-Orientation Histogram (GLOH) are robust to geometric transformations but sensitive to  photometric transformations.
\par
The proposed system uses  Local Intensity Order Pattern(LIOP) based descriptors to encode  the regions detected by the Hessian-affine covariant region detector.  In the preprocessing stage, image is smoothed by a Gaussian filter and feature position and shape are identified by Hessian-affine detector. Detected regions are normalized to circular areas of fixed diameter. These local patches are sorted based on the intensity level of the pixels and construct a histogram based on the order. 
\begin{figure}[ht]
 \centering
 \includegraphics[width=7cm]{images/liop.png}
\caption{LIOP descriptor layout. courtesy: vlfeat.org}
\label{liop}
\end{figure}

Rotation invariant is achieved by taking neighbourhood pixels of pixel $x$ in the anticlockwise direction on a circle as shown in fig \ref{liop}. In order to develop  the histogram, the identified order of intensities in the neighbourhood  of pixels will map to a linear index. Bins are constructed based on the weighted pooling of mapped linear indices  in the region.

\begin{figure}[ht]
 \centering
 \includegraphics[width=7cm]{images/liop.png}
\caption{LIOP descriptor layout. courtesy: vlfeat.org}
\label{liop}
\end{figure}

\end{document}

### 2015-03-18 vslam/odometry/digest.tex
digest v1

\documentclass{article}
\usepackage{setspace}
\usepackage[margin=.8 in]{geometry}
\usepackage{amsmath,graphicx}
\usepackage[font=small,skip=1pt]{caption}
\usepackage{float}
\captionsetup[figure]{font=small,skip=1pt}
\author{\#Authors}
\title{Stereo odometry based on  Local Intensity Order Pattern}
\onehalfspacing
\begin{document}
\maketitle
\begin{abstract}
New generation autonomous vehicles use different data fusion techniques to solve the Simultaneous Localization And Mapping (SLAM) problems in urban terrains.  However, the majority of the implementations uses high-cost sensors like LIDAR to obtain a high accuracy map. In this paper, we  present a novel method  to solve this problem using sequences of stereo images. Our approach uses Local Intensity Order Pattern (LIOP) based  feature descriptors to  overcome the problem of monotonic intensity changes and affine transformations of detected features. Egomotion of the vehicle is estimated using correspondence of features on the consecutive frames. Estimated motion parameters are then corrected using an extended Kalman filter. Depth of the detected features is calculated using stereo triangulation. Mahalanobis distance  is used to avoid outliers in the detected features.
The accuracy of  the proposed method is  evaluated using the measurements from a  high accurate inertial navigation system. Method is tested using the odometry data set of the KITTI Vision Benchmark Suite.

\end{abstract}
\section{Introduction}

 Precise  pose estimation is  the key prerequisite for  achieving autonomous driving of any mobile robotics systems. However, commonly dead-reckoning methods are prone to accumulation of error over time. In this work, we concentrate on a method called visual odometry, which uses a  camera to estimate the position of the vehicle. In order to calculate 6DOF camera motion, the system has to detect and match the features between the image frames. Depth of the features is obtained using triangular geometry between  image views and the camera baseline. Main contribution of this paper  as follows.

\begin{itemize}
\item Use of a feature descriptor which is invariant to photometric transformations.
\item Outlier rejection scheme based on Mahalanobis distance.
\end{itemize}
\par
Our experimental results shows, rotational error at high speed will be reduced significantly by the use of  proposed feature descriptor, which is invariant to  photometric transformations such as image blur.

\section{Related Literature}

Visual odometry has been gaining attention of the research community over the last few years. Several methods have been proposed to compute the ego-motion using stereo \cite{mandelbaum1999correlation}, \cite{mallet2000position}, \cite{Kitt2010IV}, \cite{badino2013visual} and the monocular \cite{bruss1983passive}, \cite{heeger1992subspace}, \cite{kanatani19933} \cite{wagner1999robust} sequence of images. Hernan Badino and et al. \cite{badino2013visual} propose a Method to reduce the projection error by computing the optical flow  over all past frames. Ji Zhang et al. \cite{zhang2014real} explores use of bundle adjustment to increase the accuracy. Efficient use of GPU-based pipelines to optimize a  binocular bundle adjustment algorithm is suggested by Wei Lu et al. \cite{hpvo}.

\par
Error model in stereo navigation system is proposed by Matthies et al. \cite{matthies1987error}. Their experiments showed that  3D Gaussian reduces the variance in robot position. However, in order to have a high accurate position estimation, system have to incorporate an invariant feature detection and representation method.  Scaramuzza et al. \cite{Scaramuzza2008} uses SIFT based feature description methods to achieve a better accuracy. Bernd Kitt et al. \cite{Kitt2010IV} recommends the use of RANSAC based outlier  rejection  scheme with a feature bucketing technique to select better feature points.

\section{System Overview}

The proposed system is similar to the method suggested by Bernd Kitt et al.\cite{Kitt2010IV}. However, to make the system more robust to illumination changes, specular reflection and blur   LIOP \cite{wang2011local} based  feature descriptors are introduced. To Mahalanobis distance-based outlier rejection \cite{Blanco2012} method is are used to calculate optimal correspondence between the feature points. Shortlisted feature points are projected to 3D with the help of triangulation from the camera baseline to obtain the depth. Estimated camera motion parameters are corrected using   the extended Kalman filter. An overview of the system is given in fig \ref{sv}.
\begin{figure}[ht]
 \centering
 \includegraphics[width=10cm]{images/so.eps}
\caption{System Overview}
\label{sv}
\end{figure}

\subsection{Feature extraction, description and matching }
The performance of a visual odometry system  depends on extraction and representation of features. To achieve a consistent odometry in adverse weather and lighting conditions, the descriptor must be invariant to photometric transforms such as  specular reflections, complex illumination changes and monotonic intensity changes.
However, the widely used descriptors such as Scale Invariant Feature Transform(SIFT) and Gradient Location-Orientation Histogram (GLOH) are robust to geometric transformations but sensitive to  photometric transformations.
\par
The proposed system uses  Local Intensity Order Pattern(LIOP)\cite{wang2011local} based descriptors to encode  the regions detected by the Hessian-affine covariant region detector. In the preprocessing stage, image is smoothed by a Gaussian filter and feature position and shape are identified by the Hessian-affine detector\cite{mikolajczyk2002affine}. Detected regions are normalized to circular areas of fixed diameter. These local patches are sorted based on the intensity level of the pixels and construct a histogram based on the order.

\par
Rotation invariant is achieved by taking neighbourhood pixels of pixel $x$ in the anticlockwise direction on a circle. In order to develop  the histogram, the identified order of intensities in the neighbourhood  of pixels will map to a linear index. Bins are constructed based on the weighted pooling of mapped linear indices  in the region. Extracted features are matched using the fast nearest neighbour matching algorithm. Figure \ref{match} shows randomly selected feature matches .

\begin{figure}[ht]
 \centering
 \includegraphics[width=15cm , height=4cm]{images/matchc.eps}
\caption{LIOP descriptor matches between  left and right images.}
\label{match}
\end{figure}
\subsection{Outlier rejection and State Estimation}
Mahalanobis distance is used to identify the optimal set of the detected feature matches. It is used to calculate the distance between a feature and the overall distribution of the feature correspondence. The Mahalanobis distance \cite{de2000mahalanobis} of an observation $x = ( x_1, x_2, x_3, \dots, x_N )^T$ from a group of observations with mean $\mu = ( \mu_1, \mu_2, \mu_3, \dots , \mu_N )^T$ and covariance matrix $S$ is defined as:

\begin{equation}D_M(x) = \sqrt{(x - \mu)^T S^{-1} (x-\mu)}.\end{equation}

These features are projected to 3D using the triangular geometry between the image views and camera baseline with help of camera intrinsic parameters. This process is repeated over image frames to measure the motion of the camera. Estimated motion parameter are corrected using an extended Kalman filter.

\section{Results and Observations}
Proposed method is tested using KITTI vision benchmark suite\cite{Geiger2012CVPR}  and estimated position  and errors for the sequence-01 are given in figure [3-7]. Algorithms are implemented using C++ with help of VLFEAT library in an  i5-3210M, 2.5Ghz CPU.Following are the observations from this empirical method.

\begin{itemize}
\item Use of LIOP based feature descriptors will improve the accuracy of the estimation, but the computational cost is high. 
\item  LIOP features are invariant to the photometric transformation such as illumination changes. However, It can be further improved in the context of visual odometry.
\end{itemize}
\begin{figure}[ht]
 \centering
 \includegraphics[width=10cm ]{images/01.eps}
\caption{Estimated path.}
\label{match}
\end{figure}
\begin{figure}[H]
    \centering
    \begin{minipage}{.5\textwidth}

        \centering
        \includegraphics[width=8cm]{images/01_rl.eps}
        \vspace{-1.5em}
        \caption{Rotation Error  vs Path Length}
        \label{a}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_rs.eps}
         \vspace{-1.5em}
        \caption{Rotation Error  vs Speed}
        \label{b}
    \end{minipage}
    \centering
    \begin{minipage}{.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_tl.eps}
         \vspace{-1.5em}
        \caption{Translation Error  vs Path Length}
        \label{c}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_ts.eps}
         \vspace{-1.5em}
        \caption{Translation Error  vs Speed}
        \label{fd}
    \end{minipage}
\end{figure}
\section{conclusion}
 In this paper, we presented a method to estimate ego-motion using visual odometry. This technique relies on  LIOP based feature detector.
Majority of the data set available to evaluate the system does not include the images in a bad weather condition or night driving. So this method needs to explore further with the help of more challenging image datasets with specular reflections and complex illumination changes.

\bibliographystyle{IEEEbib}
\bibliography{ref}
\end{document}

### 2015-04-28 reading_slam/report.tex
initial

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{setspace}
\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset  -.85in

\pagestyle{empty}

\begin{document}
\doublespacing
\section{Introduction}
The Simultaneous Localisation and Mapping (SLAM) problem asks if it is possible for a mobile robot to be placed at an unknown location in an unknown environment and for the robot to incrementally build a consistent map of this environment while simultaneously determining its lo- cation within this map. A solution to the SLAM problem has been seen as a ‘holy grail’ for the mobile robotics community as it would provide the means to make a robot truly autonomous. The solution of the SLAM problem has been one of
the notable successes of the robotics community over the past decade. SLAM has been formulated and solved as a theoretical problem in a number of different forms. SLAM has also been implemented in a number of different domains from indoor robots, to outdoor, underwater and airborne systems. At a theoretical and conceptual level, SLAM can now be considered a solved problem. However, substantial issues remain in practically realizing more general SLAM solutions and notably in building and using perceptually rich maps as part of a SLAM algorithm.
\subsection{History of the SLAM Problem}

The genesis of the probabilistic SLAM problem occurred
at the 1986 IEEE Robotics and Automation Conference held in San Francisco. This was a time when probabilis- tic methods were only just beginning to be introduced into both robotics and AI. A number of researchers had been looking at applying estimation-theoretic methods to mapping and localisation problems; these included Peter Cheeseman, Jim Crowley, and Hugh Durrant-Whyte. Over the course of the conference many paper table cloths and napkins were filled with long discussions about consistent mapping. Along the way, Raja Chatila, Oliver Faugeras, Randal Smith and others also made useful contributions to the conversation.
\par The result of this conversation was a recognition that consistent probabilistic mapping was a fundamental prob- lem in robotics with major conceptual and computational issues that needed to be addressed. Over the next few years a number of key papers were produced. Work by Smith and Cheesman  and Durrant-Whyte  established a statistical basis for describing relationships between land- marks and manipulating geometric uncertainty. A key el- ement of this work was to show that there must be a high degree of correlation between estimates of the location of different landmarks in a map and that indeed these corre- lations would grow with successive observations.
\par At the same time Ayache and Faugeras  were undertaking early work in visual navigation, Crowley  and Chatila and Laumond  in sonar based navigation of mobile robots using Kalman filter-type algorithms. These two strands of research had much in common and resulted soon after in the landmark paper by Smith, Self and Cheese- man . This paper showed that as a mobile robot moves through an unknown environment taking relative observa- tions of landmarks, the estimates of these landmarks are all necessarily correlated with each other because of the common error in estimated vehicle location . The im- plication of this was profound: A consistent full solution to the combined localisation and mapping problem would require a joint state composed of the vehicle pose and every landmark position, to be updated following each landmark observation. In turn, this would require the estimator to employ a huge state vector (of order the number of land- marks maintained in the map) with computation scaling as the square of the number of landmarks.
 Crucially, this work did not look at the convergence properties of the map or its steady-state behavior. Indeed, it was widely assumed at the time that the estimated map errors would not converge and would instead exhibit a ran- dom walk behavior with unbounded error growth. Thus, given the computational complexity of the mapping prob- lem and without knowledge of the convergence behavior of the map, researchers instead focused on a series of approxi- mations to the consistent mapping problem solution which assumed or even forced the correlations between landmarks to be minimized or eliminated so reducing the full filter to a series of decoupled landmark to vehicle filters Also for these reasons, theoretical work on the combined localisation and mapping problem came to a temporary halt, with work often focused on either mapping or localisation as separate problems.
\section{Formulation and Structure of the SLAM problem}
SLAM is a process by which a mobile robot can build
a map of an environment and at the same time use this map to deduce it’s location. In SLAM both the trajectory of the platform and the location of all landmarks are esti- mated on-line without the need for any a priori knowledge of location.
A.
\begin{figure}[ht]
    \centering
    \includegraphics[width=160mm]{structure.jpg}
    \caption{The essential SLAM problem.}
    \label{slamstruct}
\end{figure} Consider a mobile robot moving through an environment
taking relative observations of a number of unknown landmarks using a sensor located on the robot as shown in Figure \ref{slamstruct}. At a time instant k, the following quantities are defined:
\begin{itemize}
\item $x_k$: The state vector describing the location and orientation of the vehicle.
\item $u_k$: The control vector, applied at time $k-1$ to drive the vehicle to a state $x_k$ at time $k$.
\item $m_i$: A vector describing the location of the $i_{th}$ landmark whose true location is assumed time invariant.
\item $z_{ik}$ : An observation taken from the vehicle of the location of the ith landmark at time $k$. When there are multiple
landmark observations at any one time or when the specific landmark is not relevant to the discussion, the observation
will be written simply as $z_k$ .\\
In addition, the following sets are also defined:
\item $X_{0:k} = {x_0,x_1,\dots,x_k} = {X_{0:k-1},x_k}$ : The history of vehicle locations.
\item $U_{0:k} = {u_1,u_2,\dots,u_k} = {U_{0:k-1},u_k}$ : The history of control inputs.
\item $m= {m_1,m_2, \dots ,m_n}$ The set of all landmarks. $Z_{0:k} = {z_1, z_2,\dots,z_k} = {Z_{0:k−1}, z_k}$ : The set of all landmark observations.
\end{itemize}
\subsection{Probabilistic SLAM}
In probabilistic form, the Simultaneous Localisation and Map Building (SLAM) problem requires that the probability distribution.
\begin{equation}
P(x_k,m|Z_{0:k},U_{0:k},x_0)
\end{equation}
be computed for all times $k$. This probability distribution describes the joint posterior density of the landmark locations and vehicle state (at time k) given the recorded observations and control inputs up to and including time k together with the initial state of the vehicle. In general, a recursive solution to the SLAM problem is desirable. Starting with an estimate for the distribution
$P(x_{k−1},m| Z_{0:k−1},U_{0:k−1})$ at time $k-1$, the joint posterior, following a control $u_k$ and observation $z_k$, is computed using Bayes Theorem. This computation requires that a state transition model and an observation model are defined describing the effect of the control input and observation respectively.
\par The observation model describes the probability of making an observation zk when the vehicle location and landmark locations are known, and is generally described in the form 
\begin{equation}
P(z_k | x_k,m)
\end{equation}
It is reasonable to assume that once the vehicle location and map are defined, observations are conditionally independent given the map and the current vehicle state.
\par The motion model for the vehicle can be described in terms of a probability distribution on state transitions in the form
\begin{equation}
P(x_k | x_{k-1},u_k)
\end{equation}
That is, the state transition is assumed to be a Markov process in which the next state $x_k$ depends only on the immediately proceeding state $x_k−1$ and the applied control $u_k$, and is independent of both the observations and the map.
The SLAM algorithm is now implemented in a standard two-step recursive (sequential) prediction (time-update) correction (measurement-update) form:
\begin{equation}
P(x_k,m| Z_{0:k-1},U_{0:k},x_0)=\int P(x_k | x_{k-1},u_k)*P(x_{k-1},m| Z_{0:k-1},U_{0:k-1},x_0)dx_{k-1}
\end{equation}
Measurement Update
\begin{equation}
P(x_k,m| Z_{0:k},U_{0:k},x_0)=\frac{P(z_k | x_k,m)P(x_k,m| Z_{0:k-1},U_{0:k},x_0)}{ P(z_k | Z_{0:k-1},U_{0:k})}
\end{equation}
Equations 4 and 5 provide a recursive procedure for calculating the joint posterior $P(x_k,m| Z_{0:k},U_{0:k},x_0)$ for the robot state $x_k$ and mapmat a time k based on all observations $Z_{0:k}$ and all control inputs $U_{0:k}$ up to and including time k. The recursion is a function of a vehicle model $P(x_k | x_{k-1},u_k)$ and an observation model $P(z_k | x_k,m)$. It is worth noting that the map building problem may be formulated as computing the conditional density $P(m| X_{0:k},Z_{0:k},U_{0:k})$. This assumes that the location of the vehicle $x_k$ is known (or at least deterministic) at all times, subject to knowledge of initial location. A map
m is then constructed by fusing observations from different locations. Conversely, the localisation problem may be formulated as computing the probability distribution $P(x_k | Z_{0:k},U_{0:k},m)$. This assumes that the landmark lo- cations are known with certainty and the objective is to compute an estimate of vehicle location with respect to these landmarks.
\section{Solutions to the SLAM Problem}
Solutions to the probabilistic SLAM problem involve finding an appropriate representation for the observation model Equation 2 and motion model Equation 3 which allows efficient and consistent computation of the prior and posterior distributions in Equations 4 and 5. By far the most common representation is in the form of a state-space model with additive Gaussian noise, leading to the use of the extended Kalman filter (EKF) to solve the SLAM problem. One important alternative representation is to describe the vehicle motion model in Equation 3 as a set of samples of a more general non-Gaussian probability distribution. This leads to the use of the RaoBlackwellised particle filter, or Fast-SLAM algorithm, to solve the SLAM problem as described in Section IV-B. While EKF-SLAM and FastSLAM are the two most important solution methods, newer alternatives, which offer much potential, have been proposed including the use of the information state form.
\subsection{EKF-SLAM}
The basis for the EKF-SLAM method is to describe the vehicle motion in the form.
\begin{equation}
P(x_k | x_{k-1},u_k)\iff x_k = f(x_{k−1},u_k)+w_k
\end{equation}
where $f(·)$ models vehicle kinematics and where $w_k$ are additive, zero mean uncorrelated Gaussian motion disturbances with covariance $Q_k$. The observation model is described in the form
\begin{equation}
P(z_k | x_k,m)\iff z(k) = h(x_k,m)+vk
\end{equation}
where $h(·)$ describes the geometry of the observation and where $v_k$ are additive, zero mean uncorrelated Gaussian
observation errors with covariance $R_k$.
This EKF-SLAM solution is very well known and inherits 
many of the same benefits and problems as the standard EKF solutions to navigation or tracking problems. Four of the key issues are briefly discussed here:
\par \emph{Convergence}:
 In the EKF-SLAM problem, convergence of the map is manifest in the monotonic convergence of the determinant of the map covariance matrix  and all land-mark pair sub-matrices, toward zero. The individual land-mark variances converge toward a lower bound determined by initial uncertainties in robot position and observations.
 \par \emph{Computational Effort}: The observation update step requires that all landmarks and the joint covariance matrix be updated every time an observation is made. Naively, this means computation grows quadratically with the num- ber of landmarks. There has been a great deal of work undertaken in developing efficient variants of the EKF-SLAM solution and real-time implementations with many thousands of landmarks have been demonstrated .
\par \emph{Data Association}: The standard formulation of the EKF-SLAM solution is especially fragile to incorrect association of observations to landmarks. The 'loop-closure' problem, when a robot returns to reobserve landmarks after a large traverse, is especially difficult. The association problem is compounded in environments where landmarks are not simple points and indeed look different from different view-points. 
\par \emph{Non-linearity}: EKF-SLAM employs linearised models of non-linear motion and observation models and so inherits many caveats. Non-linearity can be a significant problem in EKF-SLAM and leads to inevitable, and sometimes dramatic, inconsistency in solutions . Convergence and consistency can only be guaranteed in the linear case.
\section{Rao-Blackwellised Filter}
The FastSLAM algorithm, introduced by Montemerlo et al.  marked a fundamental conceptual shift in the design of recursive probabilistic SLAM. Previous efforts focused on improving the performance of EKF-SLAM, while retaining its essential linear Gaussian assumptions. Fast-SLAM with its basis on recursive Monte Carlo sampling, or particle filtering, was the first to directly represent the non-linear process model and non-Gaussian pose distribu- tion.4 This approach was influenced by earlier probabilistic mapping experiments of Murphy  and Thrun
\par The high dimensional state-space of the SLAM problem makes direct application of particle filters computationally infeasible. However, it is possible to reduce the sample-space by applying Rao-Blackwellisation (R-B), whereby a joint state is partitioned according to the product rule $P(x_1,x_2) = P(x_2 | x_1)P(x_1) and, if P(x_2 | x_1)$ can be represented analytically, only $P(x_1)$ need be sampled $x^{(i)}\sim 1 ∼ P(x_1)$. The joint distribution, therefore, is represented by the set {x(i)
1 ,P(x2 | x(i)
1 )}N i and statistics
such as the marginal
\end{document}

### 2015-05-12 llncs2e/main.tex
springer template started

--- 2015-01-31 deep_conv_net_survey/main.tex
@@
 % Template for ICIP-2015 paper; to be used with:
-%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
-%          IEEEbib.bst - IEEE bibliography style file.
-% --------------------------------------------------------------------------
-\documentclass{article}
+\documentclass{llncs}
 
-\usepackage{spconf,amsmath,graphicx}
+\usepackage{amsmath,graphicx}
 \usepackage{caption}
@@
 \title { On Deep Convolutional networks for large scale image classification}
-%
-% Single address.
-% ---------------
-\name{Mahesh C., Student Member, IEEE, Madhu S. Nair, Member, IEEE}
-\address{Department of Computer Science, University of Kerala, Kariavattom\\ Thiruvananthapuram-695581,
-	Kerala, India.
-}
+
 %
@@
 
-\bibliographystyle{IEEEbib}
+\bibliographystyle{splncs03.bst}
 \bibliography{refs}
@@
 % --------------------------------------------------------------------------
-\documentclass{article}
-
-\usepackage{spconf,amsmath,graphicx}
-\usepackage{caption}
-
-% Example definitions.
-% --------------------
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
-
-% Title.
-% ------
-\title { On Deep Convolutional networks for large scale image classification}
-%
-% Single address.
-% ---------------
-\name{Mahesh C., Student Member, IEEE, Madhu S. Nair, Member, IEEE}
-\address{Department of Computer Science, University of Kerala, Kariavattom\\ Thiruvananthapuram-695581,
-	Kerala, India.
-}
-%
-% For example:
-% ------------
-%\address{School\\
-%	Department\\
-%	Address}
-%
-% Two addresses (uncomment and modify for two-address case).
-% ----------------------------------------------------------
-%\twoauthors
-%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
-%	{School A-B\\
-%	Department A-B\\
-%	Address A-B}
-%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
-%	while at ...}}
-%	{School C-D\\
-%	Department C-D\\
-%	Address C-D}
-%
-
-\begin{document}
-\topmargin=0mm 
-%\ninept
-%
-\maketitle
-%
-\begin{abstract}
-Image classification is an essential to the field of computer vision  based systems and recent research in this area explores better feature extraction, feature coding, and classification.
-The purpose of this paper is to review the application of supervised  deep convolution networks in this field.
-Numerous techniques have been reported to improve the performance of the convolution networks.
-Experimental analysis shows that with a large amount of labeled data, convolution networks can learn very complex functions such as image classification.
-
-\end{abstract}
-%
-\begin{keywords}
-convolution networks, deep learning, neural networks.
-\end{keywords}
-%
-\section{Introduction}
-\label{sec:intro}
-The performance of an  image  classification system mainly depends on the  extraction and  representation of features.
-Feature representation methods like Haralick texture features \cite{Haralick1973} got attention from the research community from the earlier days of  image classification.
-However, to develop features that are invariant to position, rotation, scaling, and distortion, researchers had  to  explore the visual perception of primates.
-This research  led to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}.
-As a result, many successful image classification systems are  implemented with better accuracy \cite{lecun-89e}.
-
-Early in that stage, method like the convolutional network is limited by the  availability of labeled  data and computing infrastructure.
-Researchers are trying to overcome  this problem by many other non-parametric models such as SVM and KNN.
-But these methods couldn't give a high accuracy result  on any of the large-scale classification problem  and limited by the preprocessing technique.
-However, in the recent years, the development of  High Performance Computing (HPC) architecture such as General Purpose Graphical Processing Units (GPGPU)  accelerated the research in this field.
-Large scale image  dataset such as ImageNet \cite{imagenet}  with  millions of labeled samples is also accessible to the research community.
-These changes in data and computing, put back the convolution network with millions of parameters in track.
-
-\section{Multi-stage Hubel-Wiesel architecture}
-In 1962, Hubel DH and Wiesel TN \cite{Hubel1962}, \cite{Hubel1965a}  studied visual cortex of anesthetized cats  with   spots of white light of various shapes.
-Cells in the visual system are classified    into  simple, complex and hypercomplex.
-Simple cells are influenced  by the arrangement of  excitatory and inhibitory regions of the receptive field as well as the position of the stimulus.
-This cell receives input from cells of the lateral geniculate nucleus (LGN), which is connected to the retina.
-However, the complex cells will respond to  an appropriately  oriented stimulus regardless of the cell position in the receptive field.
-Complex cells are activated by edge, dark bar, slit and mixed stimuli.
-Hypercomplex cells are activated by edge, single-stopped (corner), double-stopped (tongue), slit (double-stopped) and dark bar (double-stopped).
-
-\par In the visual cortex, perception cells are in the  order, simple$\Longrightarrow$complex$\Longrightarrow$lower-order-hypercomplex$\Longrightarrow$higher-order-hypercomplex.
-Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant.
-There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
-\par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
-In neocognitron, cells are arranged in  a number of  cascaded structure.
-Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$.
-This network is not affected by change in position or small distortion in the shape of patterns.
-It is also capable of doing self-organization based on an unsupervised competitive learning algorithm \cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8cm]{Figures/neocognitron.eps}
-\caption{Neocognitron}
-\label{neo}
-\end{figure}
-\section{Convolutional Networks}
-\par Neocognitron was improved by  Yann LeCun \cite{lecun-86}, \cite{lecun-89e}, using backpropagation algorithm  to train the entire system.
-It uses local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance.
-A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al.
-\cite{LeCun1998}  for document recognition.
-Using \allowbreak local receptive fields, network can extract elementary visual features such as edges, end points and corners.
-These features will be combined to obtain high order features in the following layers.
-Elementary feature detectors with identical weights can be useful in different parts of the image.
-So the units with  the same set of weights are arranged in plane, and output from  the units of a plane is called  a feature map.
-Units in  a feature map perform the same operation on different parts of the same image.
-A convolution layer is composed of the set of feature maps with differently weighed units.
-In the implementation, a unit in the feature map scans the image and store the states in the feature map.
-This operation is equivalent to convolution with a kernel composed of a  set of weights and image.
-
-\par
-A typical convolutional  network is composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
-\begin{figure}[ht]
-
- \includegraphics[width=8cm]{Figures/convent.eps}
-\caption{A typical convolutional network architecture }
-\label{net}
-\end{figure}
-\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between an input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
- ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$, where $b_j$ is a trainable bias, $i$ and $j$ are  array indices, and $*$ is the convolution operator.\\
-\emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output.
-But to reduce training time with gradient descent, new implementations uses the function $max(0,x)$.
-Units with this non-linearity is called Rectified Linear Units (ReLUs) \cite{Nair2010}.\\
-\emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
-
-% -------------------------------------------------------------------------
-
-\begin{figure}[t]
-
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{Figures/org}}
-%  \vspace{2.0cm}
-  \centerline{Input image}\medskip
-\end{minipage}
-%
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{Figures/first}}
-%  \vspace{1.5cm}
-  \centerline{Output - first component }\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{Figures/second}}
-%  \vspace{1.5cm}
-  \centerline{Output - second component}\medskip
-\end{minipage}
-%
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{Figures/third}}
-%  \vspace{1.5cm}
-  \centerline{Output - third component}\medskip
-\end{minipage}
-%
-
-\caption{Output of a randomly initialized convolution filter.
-}
-\label{fig:res}
-%
-\end{figure}
-
-But this architecture was limited by the availability of computing power and  sample data sets. 
-%2012
-
-\section {Deep convolutional networks}
-In the last few years, convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST \cite{Ciresan:2012g}, CIFAR-10, CIFAR-100, SVHN \cite{lee2014deeply}, and STL-10 \cite{deepfwd}.
-Krizhevsky, et al.
-\cite{Krizhevsky2012a} proposed a network  of 60 million parameters and 650,000 neurons, with five convolutional layers followed by max-pooling layers and three fully-connected layers.
-Data set used in this experiment was a subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC) \cite{imagenet} and reported an error rate of 15.3\%.
-ILSVRC data set includes 1.2 million images that contain 1,000 categories.
-This network uses rectifier  as the function in neurons.
-Even if it shows improvement in speed, this  ill-conditioned parameterization must be studied further to understand the effect in very large networks.
-
-%2013
-
-\subsection{Network in Network }
-Inspired by the work of Ian J.
-Goodfellow et al..\cite{Goodfellow2013} on max out networks,  Min Lin et al.
-\cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network.
-Using multilayer perceptron instead of voting to approximate convex functions of each  local patches may result in a good accuracy; but this is equivalent to moving linear separability problem into another hyperspace.
-So, if the input is in high frequency, this will end up in modeling large number of hidden layers and make the network structure more dependent on the problem.
-It will diverge the idea of the convolution network from \emph{learn anything} to a \emph{local search}.
-
-\subsection{Visualizing Convolutional Networks}
-
-Matthew D.
-Zeiler and Rob Fergus \cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of convolutional networks and used it as a diagnostic tool to improve  the model proposed by Krizhevsky et al.
-\cite{Krizhevsky2012a}.
-This method helped  them  to understand  the activation in the feature maps with respect to the input patterns.
-It shows that Krizhevsky et al.'s architecture does not have  enough mid frequency coverage in the first layer filters and causes aliasing artifacts by large stride in the first layer convolutions.
-Authors solved this problem by decreasing filter size to $7\times7$ and reducing stride to 2.
-This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.
-These  techniques might be more useful if it can relate to any of the learning formulations instead of vague approximations of a non-invertible function.
-
-%2014
-
-\subsection{Spatial Pyramid Pooling in Deep Convolutional Networks}
-Instead of using fixed input size in convolutional networks, Kaiming He et al.
-\cite{He2014} suggested  the use of a spooling strategy called  Spatial Pyramid Pooling (SPP) \cite{Grauman2005} \cite{1641019} to avoid cropping or warping of images.
-It introduced a new layer on top of the convolution layer and performed aggregation  based on Bag-of-Words (BoW) model.
-However, the classical backpropagation training methods expect layers to have a fixed   size.
-This problem can be solved by using two fixed size networks with shared parameters and switch the network on alternate epochs.
-Network was trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
-\par 
-This implementation improves the performance of baseline architectures including ZF-5 \cite{Zeiler2013}, Convnet \cite{Krizhevsky2012a} and Overfeat-5/7.
-Even if  the accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations, all these methods will increase both time and space complexity of the system.
-%
-
-\subsection{Going deeper with convolutions }
-Christian Szegedy et al.
-\cite{Szegedy} proposed a network named GoogLeNet with receptive field (input layer) of size $244\times244$ with the number of layers around 100.
-Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on the number of epochs.
-Learning procedure took advantage of  model and data-parallelism in a CPU-based cluster environment.
-This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set.
-The experimental analysis shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
-Even if higher depth will increase the accuracy, this system will end up with implementing large number of hidden layers to increase accuracy for a high frequency input.
-
-\section{VERY DEEP CONVOLUTIONAL NETWORKS }
-Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
-Their deep network architecture comprised of fixed  size input layers, a stack of convolution layers, three Fully-Connected (FC) layers and  5 max-pooling layers for spatial pooling  over a $2 \times 2$ pixel window with stride 2.
-Hidden layers are modeled using Rectified Linear Units (ReLU) \cite{Nair2010}.
-On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs.
-Network is trained using multinomial logistic regression  based on backpropagation with momentum of 0.9 and  batch size  256.
-\par
-It has been observed that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number of epochs and gain significant improvement in accuracy.
-This model of the convolution network does not differ from the classical architecture proposed by LeCun et al.
-\cite{LeCun1998}.
-This implementation results in a significant improvement in accuracy with  an error rate of 6.8\% in ILSVRC 2014 of ImageNet.
-
-\begin{subsection}{Scaling up Image Classification}
-The latest attempt in image classification with an error rate of 5.98\% in ImageNet data set is reported by Ren Wu et al.
-\cite{Wu2015} of Baidu research.
-They developed an end to end deep learning  system named Deep Image.
-It uses a highly optimized parallel algorithm to implement large deep neural network with augmented input data.
-The network is trained using Stochastic Gradient Descent algorithms (SGD) on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs.
-System  uses an InfiniBand  network for interconnections.
-Parallelism strategies used in this network are model-data parallelism and data parallelism.
-These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al.
-\cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems.
-However, it is not easy to extend the same strategies to multiple GPU clusters because of the communication overhead.
-The major objective is to minimize network data transfers and dynamic computation.
-So it uses butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation.
-These approaches shows that model-data parallelism is better when number of GPUs is less than 16.
-Implementation of Data parallelism in a large number of GPU cluster is better because of the constant communication requirements.
-\par
-Data augmentation techniques are used to increase the number of labeled images in the training set.
-This includes color casting, vignetting, lens distortion, rotation, flipping and cropping.
-But this data augmentation techniques does not solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
-\begin{table*}[ht]
-\captionsetup{justification=centering,belowskip=-2pt,aboveskip=-2pt}
-\caption[]{ Comparative analysis of state-of-the-art deep convolutional network based image classification algorithms using ILSVRC dataset.}
- \begin{tabular}{ | p{2.7cm} | l | p{1.4cm} |p{1.3cm} |p{.8cm} |p{1.3cm} |p{1.1cm} |p{5cm}|}
-
-    \hline
-\textbf{Team}	&\textbf{Year}	&\textbf{Data Augmentation}	&\textbf{Scalable over network}	&\textbf{Time taken}	&\textbf{Hardware}	&\textbf{Error rate} &\textbf{Observations}
-\\ 
-\hline
-Ren Wu et al. \cite{Wu2015}&2015&Aggressive&Yes&8.8 hours&Multi-GPU Cluster&5.98\%&Aggressive augmentation  will make the problem dependent on data set.\\
-\hline
-Karen Simonyan et al. \cite{Arge2015}&2014&Minimum&No&3 weeks&Multi-GPU&6.80\% &Effect of small convolution filter in low frequency domain need to be studied.\\
-\hline
-Christian Szegedy et al. \cite{Szegedy}&2014&Minimum&Yes&1 week&CPU Cluster&6.67\% &Inserting more layers will make system depend on the data set.\\
-\hline
-Kaiming He et al. \cite{He2014}&2014&Minimum&No&4 weeks	&Single GPU	&8.06\% &Good method, but higher time complexity.\\
-\hline
-Matthew D. Zeiler et al. \cite{Zeiler2013}&2013&Minimum&No&12 days&Single GPU&11.74\% & Visualizations are not possible in very deep network.\\
-\hline
-Min Lin et al. \cite{Lin2013}&2013&Minimum&No&12 days&Single GPU&12.95\% &Inserting more layers will over-fit the system.\\
-\hline
-Krizhevsky, et al.\cite{Krizhevsky2012a}&2012&Minimum&No&6 days	&Multi-GPU&15.30\%&Effect of rectifier must be studied further.\\
-\hline
-
-\end{tabular}
-\label{table_cp}
-\end{table*}
-\par
- Major contribution of this work is the demonstration of tremendous computational power required to  achieve high accuracy in image classification.
-It also shows that augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
- \end{subsection}
- \section {Observations}
-In recent years, the research community has reported several image classification algorithms based on deep convolutional network which gives less rate.
-A comparative analysis of recent futuristic deep convolutional networks is shown in Table \ref{table_cp}.
-  Ren Wu et al.
-\cite{Wu2015} uses aggressive data argumentation and high computational power to reduce the computational time and error rate.
-Karen Simonyan et al.
-\cite{Arge2015} work shows, error rate can be reduced using small convolution filters.
-Christian Szegedy  et al.
-\cite{Szegedy} and Min Lin et al.
-\cite{Lin2013} introduces a set of hidden layers to model local patches.
-Kaiming He et al.
-\cite{He2014} uses a different pooling technique to reduce the error rate.
-Krizhevsky, et al.
-\cite{Krizhevsky2012a}  introduces  rectifier  as the neuron function.
-Although significant progress has been made in the last few years, there is still room for further research and improvement.
-Major observations from our study are listed below.
- \begin{itemize}
- \itemsep0pt 
- \item  Wisely chosen data  augmentation techniques can increase the performance of the network. But need to be tested with multiple data set.
- \item Data parallelism and model parallelism can increase the speed of the training process. This area can be exploited further to increase the speed of the training process.
- \item Greater depth with small convolution filters will improve the accuracy. But, response to different frequency input must be studied.
- \item Performance of the network will get improved if images at difference scales are used for training.
- \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural level may reduce the error rate. 
-\end{itemize}
-\section{conclusion}
-This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance.
-Majority of the reviewed  works are reported from ImageNet Large-Scale Visual Recognition Challenge.
-These networks can only be trained using very expensive computing resources such as multiGPU cluster  to achieve more accuracy on large data sets.
-So  this research heavily depends on other research domains such as parallel algorithms, computer networks and multicore architecture.
-Because of the heavy computational requirements, it is not easy to apply this method directly  to the small level computing platforms such as embedded systems and application level  processors.
-On the other side, these methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.
-
-\bibliographystyle{IEEEbib}
-\bibliography{refs}
-
-\end{document}

### 2015-05-12 vslam/odometry/digest.tex
springer template started

@@
 \usepackage{float}
+\usepackage{authblk}
 \captionsetup[figure]{font=small,skip=1pt}
-\author{\#Authors}
+
 \title{Stereo odometry based on  Local Intensity Order Pattern}
+
+\author[1]{Mahesh C.}
+\author[1]{Aswathy A. L.}
+\author[2]{James Joy}
+\affil[1]{Department of Computer Science, University of Kerala, Kariavattom, Thiruvananthapuram-695581,Kerala, India}
+\affil[2]{Tata Elxsi Limited, Technopark Campus, Kariavattom, Thiruvananthapuram-695581,Kerala, India}
+
+\date{}
 \onehalfspacing
@@
 However, the majority of the implementations uses high-cost sensors like LIDAR to obtain a high accuracy map.
-In this paper, we  present a novel method  to solve this problem using sequences of stereo images.
+In this paper, we  present a method  to solve this problem using sequences of stereo images.
 Our approach uses Local Intensity Order Pattern (LIOP) based  feature descriptors to  overcome the problem of monotonic intensity changes and affine transformations of detected features.
-Egomotion of the vehicle is estimated using correspondence of features on the consecutive frames.
+Ego-motion of the vehicle is estimated using correspondence of features on the consecutive frames.
 Estimated motion parameters are then corrected using an extended Kalman filter.
@@
 The proposed system is similar to the method suggested by Bernd Kitt et al.\cite{Kitt2010IV}.
-However, to make the system more robust to illumination changes, specular reflection and blur   LIOP \cite{wang2011local} based  feature descriptors are introduced.
-To Mahalanobis distance-based outlier rejection \cite{Blanco2012} method is are used to calculate optimal correspondence between the feature points.
+However, to make the system more robust to illumination changes, specular reflection and blur, LIOP \cite{wang2011local} based feature descriptors are introduced.
+In the preprocessing stage, image is smoothed by a Gaussian filter and feature position and shape are identified by the Hessian-affine detector\cite{mikolajczyk2002affine}.
+Mahalanobis distance-based outlier rejection \cite{Blanco2012} method is used to calculate optimal correspondence between the feature points.
 Shortlisted feature points are projected to 3D with the help of triangulation from the camera baseline to obtain the depth.
 Estimated camera motion parameters are corrected using   the extended Kalman filter.
-An overview of the system is given in fig \ref{sv}.
+An overview of the proposed system is given in Figure \ref{sv}.
 \begin{figure}[ht]
@@
 The proposed system uses  Local Intensity Order Pattern(LIOP)\cite{wang2011local} based descriptors to encode  the regions detected by the Hessian-affine covariant region detector.
-In the preprocessing stage, image is smoothed by a Gaussian filter and feature position and shape are identified by the Hessian-affine detector\cite{mikolajczyk2002affine}.
 Detected regions are normalized to circular areas of fixed diameter.
@@
 \par
-Rotation invariant is achieved by taking neighbourhood pixels of pixel $x$ in the anticlockwise direction on a circle.
+Rotation invariant is achieved by considering a circular disk of neighbourhood pixels of pixel $x$ in the anticlockwise direction on a circle.
 In order to develop  the histogram, the identified order of intensities in the neighbourhood  of pixels will map to a linear index.
@@
 Extracted features are matched using the fast nearest neighbour matching algorithm.
-Figure \ref{match} shows randomly selected feature matches .
+Figure \ref{lmatch} shows randomly selected feature matches .
 
@@
  \centering
- \includegraphics[width=15cm , height=4cm]{images/matchc.eps}
+ \includegraphics[width=12cm , height=2.6cm]{images/matchc.eps}
 \caption{LIOP descriptor matches between  left and right images.}
-\label{match}
+\label{lmatch}
 \end{figure}
@@
 \section{Results and Observations}
-Proposed method is tested using KITTI vision benchmark suite\cite{Geiger2012CVPR}  and estimated position  and errors for the sequence-01 are given in figure [3-7].
-Algorithms are implemented using C++ with help of VLFEAT library in an  i5-3210M, 2.5Ghz CPU.Following are the observations from this empirical method.
+Proposed method is tested using KITTI vision benchmark suite\cite{Geiger2012CVPR}.
+Figure \ref{rep} and \ref{res} shows the rotation error of the estimated path.
+Figure \ref{tep} and \ref{tes} shows the translation error of the estimated path.
+Estimated path and ground truth are compared in Figure \ref{ep}.
+Algorithms are implemented using C++ with help of VLFeat  library in an  INTEL i5-3210M, 2.5Ghz CPU.
+Following are the observations from this empirical method.
 
@@
  \centering
- \includegraphics[width=10cm ]{images/01.eps}
+ \includegraphics[width=9cm ]{images/01.eps}
 \caption{Estimated path.}
-\label{match}
+\label{ep}
 \end{figure}
@@
         \caption{Rotation Error  vs Path Length}
-        \label{a}
+        \label{rep}
     \end{minipage}%
@@
         \caption{Rotation Error  vs Speed}
-        \label{b}
+        \label{res}
     \end{minipage}
@@
         \caption{Translation Error  vs Path Length}
-        \label{c}
+        \label{tep}
     \end{minipage}%
@@
         \caption{Translation Error  vs Speed}
-        \label{fd}
+        \label{tes}
     \end{minipage}

### 2015-05-12 llncs2e/main.tex
changed to lncs templates, 2 figs removed

@@
 
+\addtolength{\parskip}{-.1mm}
 % Example definitions.
@@
 % ------
-\title { On Deep Convolutional networks for large scale image classification}
-
+\title { On Deep Convolutional Networks for Large Scale Image Classification}
+\author{Mahesh C. \and  Madhu S. Nair }
+\institute{Department of Computer Science, University of Kerala, Kariavattom\\ Thiruvananthapuram-695581,
+	Kerala, India.}
 %
@@
 \begin{document}
-\topmargin=0mm 
 %\ninept
@@
 
-\section{Multi-stage Hubel-Wiesel architecture}
+\section{Multi-stage Hubel-Wiesel Architecture}
 In 1962, Hubel DH and Wiesel TN \cite{Hubel1962}, \cite{Hubel1965a}  studied visual cortex of anesthetized cats  with   spots of white light of various shapes.
@@
 Hypercomplex cells are activated by edge, single-stopped (corner), double-stopped (tongue), slit (double-stopped) and dark bar (double-stopped).
-
-\par In the visual cortex, perception cells are in the  order, simple$\Longrightarrow$complex$\Longrightarrow$lower-order-hypercomplex$\Longrightarrow$higher-order-hypercomplex.
+ In the visual cortex, perception cells are in the  order, simple$\Longrightarrow$complex$\Longrightarrow$lower-order-hypercomplex$\Longrightarrow$higher-order-hypercomplex.
 Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant.
@@
 It is also capable of doing self-organization based on an unsupervised competitive learning algorithm \cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8cm]{Figures/neocognitron.eps}
- \captionsetup{justification=centering,belowskip=0pt,aboveskip=0pt}
-\caption{Neocognitron}
-\label{neo}
-\end{figure}
+
 \section{Convolutional Networks}
@@
 
- \includegraphics[width=7cm]{Figures/convent.eps}
+ \includegraphics[width=8cm]{Figures/convent.eps}
 \caption{A typical convolutional network architecture }
@@
 But to reduce training time with gradient descent, new implementations uses the function $max(0,x)$.
-Units with this non-linearity is called Rectified Linear Units (ReLUs) \cite{Nair2010}.\\
+Units with this non-linearity is called Rectified Linear Units (ReLUs).\\
 \emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
@@
 % -------------------------------------------------------------------------
-\begin{figure}[t]
-
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=3.8cm]{Figures/org}}
-%  \vspace{2.0cm}
-  \centerline{Input image}\medskip
-\end{minipage}
-%
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=3.8cm]{Figures/first}}
-%  \vspace{1.5cm}
-  \centerline{Output - first component }\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=3.8cm]{Figures/second}}
-%  \vspace{1.5cm}
-  \centerline{Output - second component}\medskip
-\end{minipage}
-%
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=3.8cm]{Figures/third}}
-%  \vspace{1.5cm}
-  \centerline{Output - third component}\medskip
-\end{minipage}
-%
-\caption{Output of a randomly initialized convolution filter.
-}
-\label{fig:res}
-%
-\end{figure}
 
@@
 
-\section {Deep convolutional networks}
+\section {Deep Convolutional Networks}
 In the last few years, convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST \cite{Ciresan:2012g}, CIFAR-10, CIFAR-100, SVHN \cite{lee2014deeply}, and STL-10 \cite{deepfwd}.
@@
 Network was trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
-\par 
 This implementation improves the performance of baseline architectures including ZF-5 \cite{Zeiler2013}, Convnet \cite{Krizhevsky2012a} and Overfeat-5/7.
@@
 
-\subsection{Going deeper with convolutions }
+\subsection{Going Deeper with Convolutions }
 Christian Szegedy et al.
@@
 
-\section{VERY DEEP CONVOLUTIONAL NETWORKS }
+\section{Very Deep Convolutional Networks}
 Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters.
 Their deep network architecture comprised of fixed  size input layers, a stack of convolution layers, three Fully-Connected (FC) layers and  5 max-pooling layers for spatial pooling  over a $2 \times 2$ pixel window with stride 2.
-Hidden layers are modeled using Rectified Linear Units (ReLU) \cite{Nair2010}.
+Hidden layers are modeled using Rectified Linear Units (ReLU).
 On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs.
 Network is trained using multinomial logistic regression  based on backpropagation with momentum of 0.9 and  batch size  256.
-\par
 It has been observed that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number of epochs and gain significant improvement in accuracy.
@@
 
-\begin{subsection}{Scaling up Image Classification}
+\begin{subsection}{Scaling Up Image Classification}
 The latest attempt in image classification with an error rate of 5.98\% in ImageNet data set is reported by Ren Wu et al.
@@
 %Implementation of Data parallelism in a large number of GPU cluster is better because of the constant communication requirements.
-\par
 Data augmentation techniques are used to increase the number of labeled images in the training set.
@@
 But this data augmentation techniques  does not solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
-\centering
+
 \begin{table*}[ht]
@@
 \caption[]{ Comparative analysis of state-of-the-art deep convolutional network based image classification algorithms using ILSVRC dataset.}
- \begin{tabular}{ | p{2.7cm} | l | p{1.4cm} |p{1.1cm} |p{.8cm} |p{1.3cm} |p{1.1cm} |p{5cm}|}
+ \begin{tabular}{ | p{2cm} | p{.7cm} | p{1.5cm} |p{1.5cm} |p{1cm} |p{1.5cm} |p{1.1cm} |p{3cm}|}
 
     \hline
-\textbf{Team}	&\textbf{Year}	&\textbf{Data Augmentation}	&\textbf{Scalable over network}	&\textbf{Time taken}	&\textbf{Hardware}	&\textbf{Error rate} &\textbf{Observations}
+Team	&Year	&Data Augmentation	&Scalable over network	&Time taken	&Hardware	&Error rate &Observations
 \\ 
 \hline
+
 Ren Wu et al. \cite{Wu2015}&2015&Aggressive&Yes&8.8 hours&Multi-GPU Cluster&5.98\%&Aggressive augmentation  will make the problem dependent on data set.\\
@@
 Major observations from our study are listed below.
- \begin{itemize}
+ \begin{enumerate}
  \itemsep0em 
@@
  \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural level may reduce the error rate. 
- \end{itemize}
+ \end{enumerate}
 
-\section{conclusion}
+\section{Conclusion}
 This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance.
@@
 
-\end{document}% Template for ICIP-2015 paper; to be used with:
-%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
-%          IEEEbib.bst - IEEE bibliography style file.
-% --------------------------------------------------------------------------
+\end{document}

### 2015-05-13 llncs2e/main.tex
adjusted vspace,figs added

@@
 
-\addtolength{\parskip}{-.1mm}
+%\addtolength{\parskip}{-.1mm}
 % Example definitions.
@@
 	Kerala, India.}
-%
-% For example:
-% ------------
-%\address{School\\
-%	Department\\
-%	Address}
-%
-% Two addresses (uncomment and modify for two-address case).
-% ----------------------------------------------------------
-%\twoauthors
-%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
-%	{School A-B\\
-%	Department A-B\\
-%	Address A-B}
-%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
-%	while at ...}}
-%	{School C-D\\
-%	Department C-D\\
-%	Address C-D}
-%
 
@@
 It is also capable of doing self-organization based on an unsupervised competitive learning algorithm \cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
-
+\vspace*{-8mm}
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8cm]{Figures/neocognitron.eps}
+ \captionsetup{justification=centering,belowskip=0pt,aboveskip=0pt}
+\caption{Neocognitron}
+\label{neo}
+\end{figure}
+\vspace*{-8mm}
 \section{Convolutional Networks}
@@
 A convolution layer is composed of the set of feature maps with differently weighed units.
-In the implementation, a unit in the feature map scans the image and store the states in the feature map.
-This operation is equivalent to convolution with a kernel composed of a  set of weights and image.
 
@@
 A typical convolutional  network is composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
+\vspace*{-6mm}
 \begin{figure}[ht]
-
  \includegraphics[width=8cm]{Figures/convent.eps}
@@
 \end{figure}
+\vspace*{-6mm}
 \emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between an input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
@@
 \emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
+\begin{figure}[t]
+
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=3.8cm]{Figures/org}}
+%  \vspace{2.0cm}
+  \centerline{Input image}\medskip
+\end{minipage}
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=3.8cm]{Figures/first}}
+%  \vspace{1.5cm}
+  \centerline{Output - first component }\medskip
+\end{minipage}
+
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=3.8cm]{Figures/second}}
+%  \vspace{1.5cm}
+  \centerline{Output - second component}\medskip
+\end{minipage}
+%
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=3.8cm]{Figures/third}}
+%  \vspace{1.5cm}
+  \centerline{Output - third component}\medskip
+\end{minipage}
+%
+\caption{Output of a randomly initialized convolution filter.
+}
+\label{fig:res}
+%
+\end{figure}
 
@@
 
-But this architecture was limited by the availability of computing power and  sample data sets. 
 %2012
@@
 ILSVRC data set includes 1.2 million images that contain 1,000 categories.
-This network uses rectifier  as the function in neurons.
-Even if it shows improvement in speed, this  ill-conditioned parameterization must be studied further to understand the effect in very large networks.
 
+\vspace*{-5mm}
 %2013
@@
 So, if the input is in high frequency, this will end up in modeling large number of hidden layers and make the network structure more dependent on the problem.
-It will diverge the idea of the convolution network from \emph{learn anything} to a \emph{local search}.
-
+\vspace*{-3mm}
 \subsection{Visualizing Convolutional Networks}
-
+\vspace*{-3mm}
 Matthew D.
@@
 This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.
-These  techniques might be more useful if it can relate to any of the learning formulations instead of vague approximations of a non-invertible function.
 
@@
 Network was trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set.
-This implementation improves the performance of baseline architectures including ZF-5 \cite{Zeiler2013}, Convnet \cite{Krizhevsky2012a} and Overfeat-5/7.
-Even if  the accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations, all these methods will increase both time and space complexity of the system.
+
 %
@@
 The experimental analysis shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.
-Even if higher depth will increase the accuracy, this system will end up with implementing large number of hidden layers to increase accuracy for a high frequency input.
 
@@
 \cite{LeCun1998}.
-This implementation results in a significant improvement in accuracy with  an error rate of 6.8\% in ILSVRC 2014 of ImageNet.
 
@@
 Data augmentation techniques are used to increase the number of labeled images in the training set.
-This includes color casting, vignetting, lens distortion, rotation, flipping and cropping.
-But this data augmentation techniques  does not solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
 
-\begin{table*}[ht]
+\par
+ Major contribution of this work is the demonstration of tremendous computational power required to  achieve high accuracy in image classification.
+It also shows that augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
+ \end{subsection}
+\vspace*{-3mm}
+\begin{table*}[t]
 \captionsetup{justification=centering,belowskip=1pt,aboveskip=1pt}
@@
 \hline
-
 \end{tabular}
@@
 \end{table*}
-\par
- Major contribution of this work is the demonstration of tremendous computational power required to  achieve high accuracy in image classification.
-It also shows that augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
- \end{subsection}
  \section {Observations}
+\vspace*{-3mm}
 In recent years, the research community has reported several image classification algorithms based on deep convolutional network which gives less rate.
@@
 Major observations from our study are listed below.
+
  \begin{enumerate}
@@
 
+\vspace*{-7mm}
 \section{Conclusion}
+\vspace*{-3mm}
 This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance.
@@
 On the other side, these methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.
-
+\vspace*{-5mm}
 \bibliographystyle{splncs03.bst}
